### 2015-10-28 excercise_4/verslag.tex
exercise session 4

\documentclass[11pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\section{Interesting knowledge bases}
\begin{enumerate}

\item Musicbrainz
\item data.nobelprize.org

\end{enumerate}
\section{Interesting questions}
\begin{enumerate}
\item How many and wich European Parliants members were involved with criminal activities?
\item Wich politicians have good chances of receiving a Nobel Price?
\item  
\end{enumerate}
\end{document}

### 2015-10-28 excercise_4/verslag.tex
exercise session 4
hw2

@@
 \usepackage{amssymb}
+\usepackage{url}
 \begin{document}
@@
 \item Musicbrainz
-\item data.nobelprize.org
+\item \url{data.nobelprize.org}
+\item \url{http://datahub.io/dataset/zdb}
+\item \url{ZDB}
 
@@
 \section{Interesting questions}
-\begin{enumerate}
-\item How many and wich European Parliants members were involved with criminal activities?
-\item Wich politicians have good chances of receiving a Nobel Price?
-\item  
-\end{enumerate}
+\subsection{How many and wich European Parliants members were involved with criminal activities?}
+\subsection{Which politicians have good chances of receiving a Nobel Price?}
+\subsection{Which song came out on the birthday of a specific politician?}
+\subsection{Which politician are murdered.}
+\subsection{Which politician are stated in any document on ZDB.}
+\subsection{Which politician have the most tv/radio appearences?}
+
 \end{document}

### 2015-11-02 homework_2/hw2.tex
updated title and cleaned project
verslag

--- 2015-10-28 excercise_4/verslag.tex
@@
-\documentclass[11pt,a4paper]{article}
-\usepackage[latin1]{inputenc}
+\documentclass[12pt,a4paper]{article}
+\usepackage[utf8]{inputenc}
 \usepackage[english]{babel}
@@
 \usepackage{amssymb}
+\usepackage{url}
+\usepackage{hyperref}
+\usepackage{framed}
+
+\setlength{\parindent}{0pt}
+
+\author{
+  Katrien Laenen\\
+  \and
+  Gust Verbruggen\\
+  \and
+  Ward Schodts
+}
+\title{Knowledge \& the web: homework 2}
 \begin{document}
-\section{Interesting knowledge bases}
-\begin{enumerate}
+\maketitle
 
-\item Musicbrainz
-\item data.nobelprize.org
+The question we chose to answer is
 
-\end{enumerate}
-\section{Interesting questions}
-\begin{enumerate}
-\item How many and wich European Parliants members were involved with criminal activities?
-\item Wich politicians have good chances of receiving a Nobel Price?
-\item  
-\end{enumerate}
+\begin{center}
+%\makebox[\textwidth]{%
+\bf \large Which politicians of the European Parliament have the most television appearances?
+%}
+\end{center}
+We are interested whether politicians also publicly appear outside the European Parliament, e.g. Di Rupo in the Flemish TV show "Salamander".
+\\
+\\
+To answer this question we need the following information from the following sources:
+\begin{itemize}
+\item Speakers from ToE
+\item Appearances from LinkedTV
+\item Programmes from the BBC
+\end{itemize}
+
+We expect some issues with the LinkedTV knowledge base.
+\url{data.linkedtv.eu} contains a lot of dead links.
+If this would become an issue, we can use data from the BBC knowledge base instead.
+In the BBC knowledge base people are not really linked to a specific frahgment but rather a whole programme.
+\\
+\\
+People are linked to specific fragments using facial recognition. As we all know such algorithms are not flawless.
+\\
+\\
+Further there may be some inconsistencies for naming the speakers between the different knowledge bases. This could lead to different names for the same person.
+\\
+\\
+We will take those last two issues under consideration if they really pose a problem.
+
 \end{document}

### 2015-11-02 excercise_4/ex4.tex
updated title and cleaned project
updated excercise 4

--- 2015-10-28 excercise_4/verslag.tex
@@
 \usepackage{url}
+\usepackage{hyperref}
+\author{
+  Katrien Laenen\\
+  \and
+  Gust Verbruggen\\
+  \and
+  Ward Schodts
+}
+\title{Knowledge \& the web: exercise session 4}
 \begin{document}
+\maketitle
 \section{Interesting knowledge bases}
@@
 \item \url{http://datahub.io/dataset/zdb}
-\item \url{ZDB}
+\item \url{www.linkedtv.eu}
 
 \end{enumerate}
+
 \section{Interesting questions}
-\subsection{How many and wich European Parliants members were involved with criminal activities?}
+
+All questions involve speakers from the ToE knowledge base. by combining it with other knowledge bases, we can infer other interesting properties about them.
+
+\subsection{How many and which European Parliament members were involved with criminal activities?}
+
+DBpedia has information on criminal activities for people.
+
 \subsection{Which politicians have good chances of receiving a Nobel Price?}
+
+The nobelprize knowledgebase has information about nobel prize winners.
+By searching for similarities (trough for example DBpedia), we can maybe find out which politicians have a (high) chance of receiving a nobel prize.
+
 \subsection{Which song came out on the birthday of a specific politician?}
-\subsection{Which politician are murdered.}
-\subsection{Which politician are stated in any document on ZDB.}
-\subsection{Which politician have the most tv/radio appearences?}
+
+ToE has birth dates for speakers, so we only have to combine it with artist information from musicbrainz to find our answer.
+
+\subsection{Which politicians have a high chance of being murdered?}
+
+Freebase contains the cause of death for deceased people, so yet again by searching for similarities with the European Parliament speakers, we can see who has a high chance of being murdered.
+
+\subsection{Which European politician have published bibliographic material?}
+
+The ZDB knowledge base contains information about bibliographic resources in many languages, chances are therefore high that at least one of the European Parliamentary speakers has published such material.
+
+\subsection{Which politician have the most tv appearances?}
+
+The LinkedTV project aims to annotate media fragments with metadata, such as \emph{faces} that appear in them. We'd like to find out if one of our speakers has made such television appearance.
 

### 2015-11-03 homework_2/hw2.tex
Homework 2 finished.

@@
 \usepackage{amssymb}
-\usepackage{url}
-\usepackage{hyperref}
+\usepackage[colorlinks = true,
+			urlcolor = blue]{hyperref}
 \usepackage{framed}
+\usepackage{enumitem}
 
@@
 \end{center}
-We are interested whether politicians also publicly appear outside the European Parliament, e.g. Di Rupo in the Flemish TV show "Salamander".
+We are interested whether politicians also publicly appear outside the European Parliament, e.g. Di Rupo once appeared in the Flemish TV show "Salamander".
+
+\subsection*{Needed knowledge bases}
+To answer this question we need the following information from the following sources.
+\begin{itemize}[leftmargin = 3cm]
+\item[\textbf{ToE}] The ToE provides us with a list of international politicians, more specifically, we need all entities of class \texttt{Speaker} along with their \texttt{PoliticalFunction}.
+\item[\textbf{LinkedTV}] The LinkedTV project aims to annotate media fragments with meta-information, such as which faces appear or entities are mentioned in it.
+Primarily, we are not interested in the actual show in which politicians appear, so having all \texttt{MediaFragment}'s along with their \texttt{Face} annotations would suffice.
+Here, we should note that a \texttt{Face} from the LinkedTV ontology is equivalent to a \texttt{Person} from the FOAF ontology, and that a ToE \texttt{Speaker} is a subclass of that.
+\item[\textbf{BBC}] Already partly answering the next question, BBC also holds some information on who occurs in their programmes.
+For this, we need the \texttt{person} relation of the \texttt{Programme} class from BBC's programme ontology.
+\end{itemize}
+
+\subsection*{Expected issues}
+We might expect some issues with the LinkedTV knowledge base, browsing \url{data.linkedtv.eu} we encounter a lot of dead links.
+For example, \url{data.linkedtv.eu/spatialobject} is dead and a \texttt{Face} is a spatial object.
+If this would become an issue, we can use data from the BBC knowledge base instead.
+Here, each \texttt{Programme} also has some persons attached to it.
+This is of course far less fine-grained than the LinkedTV database, but might already give a good overview.
 \\
 \\
-To answer this question we need the following information from the following sources:
+Furthermore, there are some other small issues that may arise:
 \begin{itemize}
-\item Speakers from ToE
-\item Appearances from LinkedTV
-\item Programmes from the BBC
+	\item People are linked to specific fragments using facial recognition. As we all know, such algorithms are not flawless.
+	\item There may be some inconsistencies for naming the speakers between the different knowledge bases. This could lead to different names for the same person.
 \end{itemize}
 
-We expect some issues with the LinkedTV knowledge base.
-\url{data.linkedtv.eu} contains a lot of dead links.
-If this would become an issue, we can use data from the BBC knowledge base instead.
-In the BBC knowledge base people are not really linked to a specific frahgment but rather a whole programme.
-\\
-\\
-People are linked to specific fragments using facial recognition. As we all know such algorithms are not flawless.
-\\
-\\
-Further there may be some inconsistencies for naming the speakers between the different knowledge bases. This could lead to different names for the same person.
-\\
-\\
 We will take those last two issues under consideration if they really pose a problem.

### 2015-11-04 excercise_4/ex4.tex
Update ex4.tex
Aantal schrijffoutjes verbeterd

--- 2015-10-28 excercise_4/verslag.tex
@@
 \usepackage{amssymb}
+\usepackage{url}
+\usepackage{hyperref}
+\author{
+  Katrien Laenen\\
+  \and
+  Gust Verbruggen\\
+  \and
+  Ward Schodts
+}
+\title{Knowledge \& the web: exercise session 4}
 \begin{document}
+\maketitle
 \section{Interesting knowledge bases}
@@
 \item Musicbrainz
-\item data.nobelprize.org
+\item \url{data.nobelprize.org}
+\item \url{http://datahub.io/dataset/zdb}
+\item \url{www.linkedtv.eu}
 
 \end{enumerate}
+
 \section{Interesting questions}
-\begin{enumerate}
-\item How many and wich European Parliants members were involved with criminal activities?
-\item Wich politicians have good chances of receiving a Nobel Price?
-\item  
-\end{enumerate}
+
+All questions involve speakers from the ToE knowledge base. By combining these with other knowledge bases, we can infer other interesting properties about them.
+
+\subsection{How many and which European Parliament members were involved in criminal activities?}
+
+DBpedia contains information on criminal activities for people.
+
+\subsection{Which politicians have a good chance of receiving a Nobel Prize?}
+
+The nobelprize knowledge base holds information on Nobel Prize winners.
+By searching for similarities (through for example DBpedia) between Nobel Prize winners and politicians, we can maybe find out which politicians have a (high) chance of receiving a Nobel Prize.
+
+\subsection{Which song came out on the birthday of a specific politician?}
+
+ToE contains birth dates for speakers, so we only have to combine it with artist information from musicbrainz to find our answer.
+
+\subsection{Which politicians have a high chance of being murdered?}
+
+Freebase contains the cause of death for deceased people, so yet again by searching for similarities with the European Parliament speakers, we can see who has a high chance of being murdered.
+
+\subsection{Which European Parliament speakers have published bibliographic material?}
+
+The ZDB knowledge base contains information about bibliographic resources in many languages, chances are therefore high that at least one of the European Parliament speakers has published such material.
+
+\subsection{Which politicians have the most tv appearances?}
+
+The LinkedTV project aims to annotate media fragments with metadata, such as \emph{faces} that appear in them. We would like to find out if one of our speakers has made such television appearance.
+
 \end{document}

### 2015-11-12 homework_3/hw3.tex
Homework 3 added

--- 2015-10-28 excercise_4/verslag.tex
@@
 \usepackage{amssymb}
-\usepackage{url}
+\usepackage[colorlinks = true,
+			urlcolor = blue]{hyperref}
+\usepackage{framed}
+\usepackage{enumitem}
+
+\setlength{\parindent}{0pt}
+
+\author{
+  Katrien Laenen\\
+  \and
+  Gust Verbruggen\\
+  \and
+  Ward Schodts
+}
+\title{Knowledge and the Web: Homework 3}
 \begin{document}
-\section{Interesting knowledge bases}
-\begin{enumerate}
-
-\item Musicbrainz
-\item \url{data.nobelprize.org}
-\item \url{http://datahub.io/dataset/zdb}
-\item \url{ZDB}
-
-\end{enumerate}
-\section{Interesting questions}
-\subsection{How many and wich European Parliants members were involved with criminal activities?}
-\subsection{Which politicians have good chances of receiving a Nobel Price?}
-\subsection{Which song came out on the birthday of a specific politician?}
-\subsection{Which politician are murdered.}
-\subsection{Which politician are stated in any document on ZDB.}
-\subsection{Which politician have the most tv/radio appearences?}
+\maketitle
 

### 2015-11-12 homework_3/hw3.tex
question 1 added

@@
 \usepackage{enumitem}
+\usepackage[english]{babel}
 
-\setlength{\parindent}{0pt}
+% \setlength{\parindent}{0pt}
 
@@
 
+\begin{center}
+	\Large
+1. Which European politicians have \emph{a high chance} of receiving a Nobel Prize?
+\end{center}
+
+We emphasise \emph{a high chance} because that could use some clarification. How do we compare probabilities of receiving Nobel Prizes between arbitrary politicians?
+\par First, we build a profile of a politician.
+This should not only cover their performance in the European Parliament, other achievements and activities are probably far more interesting.
+Where are they from?
+What subjects have they worked on before or talked about in public?
+Have they received other awards?
+Perhaps they've written a book or performed research activities?
+\par Next, we attempt to build an analogous profile for Nobel Prize winners.
+Even though prizes in Peace or perhaps Literature and Economic Sciences are far more likely to be won by a politician, we'll build the model for all winners.
+\par The final step is comparing the profiles we built.
+Do we find particular similarities between a specific Nobel Prize winner and politician?
+Or, for example, we could try learning a model for a Nobel Prize winner trough machine learning and classify the politicians using this model.
+
+\subsection*{Knowledge bases}
+
+Aside from the ToE knowledge base, we need to gather as much information as possible about the people we'll build profiles for.
+
+\paragraph{\textbf{DBpedia} (\url{http://wiki.dbpedia.org/})}
+is always a good starting point.
+Coming straight from Wikipedia, it is updated daily and should thus be up-to-date all the time.
+For many projects, Wikipedia is \emph{the} go-to data source, because it contains complete information about relevant topics to our subject.
+Although it can be edited by anyone, data correctness is verified thoroughly by a team of content moderators.
+
+\paragraph{\textbf{Nobelprize.org} (\url{http://data.nobelprize.org/})} is the most complete data source concerning nobel prize winners.
+From 1901 on, it contains all nobel prizes that have been won.
+Moreover, it is maintained by the official organisation responsible for the Nobel Prize and should thus be complete and correct.
+It makes use of the FOAF and DBpedia ontologies and more importantly, laureates have a \texttt{owl:sameAs} relation with DBpedia entries.
+\vspace{1cm}
+
+\begin{center}
+	\Large
+2. Which characteristics of a politician and his country influence the amount of TV appearances he makes?
+\end{center}
+
 \end{document}

### 2015-11-12 homework_3/hw3.tex
vraag 2 begin added.
kaw

@@
 	\Large
-2. Which characteristics of a politician and his country influence the amount of TV appearances he makes?
+2. Which characteristics of a politician influence the amount of TV appearances he makes?
+\end{center}
+
+There is one specific characteristic that we really want to research. Namely: "Does the country of origin of the politician influence his TV appearences?".
+
+\begin{center}
+	\Large
+3. Which politicians have a high chance of being murdered?
 \end{center}

### 2015-11-12 homework_3/hw3.tex
data sources vraag 3

@@
 
+\paragraph{\textbf{European Union Open Data Portal} (\url{https://open-data.europa.eu/})} contains datasets about homicides and other criminal activities e.g.
+homicide offences.
+This data necessary to determine if location influences the chance of being murdered.
+
+\paragraph{\textbf{Freebase} (\url{https://www.freebase.com/})} This is a knowledge base specialized among others in well-known people.
+Because most politicians are well-known this is a interesting knowledge base.
+Furthermore in Freebase is the property \textit{cause\_of\_death} which we can use to find murders or homicides among the politicians.
+
+\paragraph{\textbf{DBpedia} (\url{http://wiki.dbpedia.org/})}
+For this question we need also some background information. As already pointed out, DBpedia is a good source for this.
 \end{document}

### 2015-11-14 homework_3/hw3.tex
Update van hw3.tex
Tekst voor vraag 3 geschreven

@@
 
+Politicians get a lot of criticism and sometimes they even get murdered.
+Of course, this can be for political reasons as well as for non-political reasons.
+The goal of this question is to predict which politicians have a high probability of being killed, by comparing them with the profiles of murdered politicians.
+We expect that the subjects they talk about and their political beliefs are the factors which have the biggest influence on this probability.
+On top of that, for politicians that live in places with high murder rates or that visit these kinds of places often, it is likely that this probability will even increase.
+
+\subsection*{Knowledge bases}
+
+Aside from the ToE knowledge base, we also need the following knowledge bases:
+
 \paragraph{\textbf{European Union Open Data Portal} (\url{https://open-data.europa.eu/})} contains datasets about homicides and other criminal activities e.g.
 homicide offences.
-This data necessary to determine if location influences the chance of being murdered.
+This data is necessary to determine if location influences the chance of being murdered.
+The European Commission maintains this website to keep this information timely and accurate.
 
-\paragraph{\textbf{Freebase} (\url{https://www.freebase.com/})} This is a knowledge base specialized among others in well-known people.
+\paragraph{\textbf{Freebase} (\url{https://www.freebase.com/})} This is an openly available knowledge base specialized among others in well-known people.
 Because most politicians are well-known this is a interesting knowledge base.
-Furthermore in Freebase is the property \textit{cause\_of\_death} which we can use to find murders or homicides among the politicians.
+Furthermore, Freebase contains the property \textit{cause\_of\_death} which we can use to find murders or homicides among the politicians.
+As such, this database is highly relevant and complete regarding this research question.
+Like Wikipedia, Freebase can be edited by anyone.
+But this also means that the information can be corrected by anyone and people make incremental improvements all the time.
+Besides this, there is a group of trusted Freebase experts which are responsible for solving such issues.
+Thus, there will be some inaccurate information in this database but we expect the database to be fairly correct.
 

### 2015-11-15 homework_3/hw3.tex
homework 3 ready to check
* laatste vraag afgewerkt
* volgorder veranderd om dbpedia en freebase niet nog eens uit te
moeten leggen
* andere typos

@@
 \usepackage[english]{babel}
+\usepackage{todonotes}
 
@@
 
-\begin{center}
-	\Large
-1. Which European politicians have \emph{a high chance} of receiving a Nobel Prize?
-\end{center}
+This document thoroughly discusses three research questions, along with the knowledge bases needed to solve them.
+When talking about ontologies, relations will be \emph{emphasised} and classes \texttt{monospaced}.
+
+\section{Which European politicians have \emph{a high chance} of receiving a Nobel Prize?}
 
@@
 Moreover, it is maintained by the official organisation responsible for the Nobel Prize and should thus be complete and correct.
-It makes use of the FOAF and DBpedia ontologies and more importantly, laureates have a \texttt{owl:sameAs} relation with DBpedia entries.
-\vspace{1cm}
+It makes use of the FOAF and DBpedia ontologies and more importantly, laureates have a \emph{owl:sameAs} relation with DBpedia entries for easy lookup of background information.
 
-\begin{center}
-	\Large
-2. Which characteristics of a politician influence the amount of TV appearances he makes?
-\end{center}
-
-There is one specific characteristic that we really want to research. Namely: "Does the country of origin of the politician influence his TV appearences?".
-
-\begin{center}
-	\Large
-3. Which politicians have a high chance of being murdered?
-\end{center}
+\section{\hyphenpenalty=10000 Which politicians have a high chance of being murdered?}
 
@@
 Of course, this can be for political reasons as well as for non-political reasons.
-The goal of this question is to predict which politicians have a high probability of being killed, by comparing them with the profiles of murdered politicians.
+The goal of this question is to predict which politicians have a high probability of being killed by comparing them with the profiles of murdered politicians.
 We expect that the subjects they talk about and their political beliefs are the factors which have the biggest influence on this probability.
@@
 
-Aside from the ToE knowledge base, we also need the following knowledge bases:
+Aside from the ToE knowledge base, we also need the following knowledge bases.
 
 \paragraph{\textbf{European Union Open Data Portal} (\url{https://open-data.europa.eu/})} contains datasets about homicides and other criminal activities e.g.
-homicide offences.
-This data is necessary to determine if location influences the chance of being murdered.
+homicide offences.\todo{2 x homicide?} This data is necessary to determine if location influences the chance of being murdered.
 The European Commission maintains this website to keep this information timely and accurate.
 
-\paragraph{\textbf{Freebase} (\url{https://www.freebase.com/})} This is an openly available knowledge base specialized among others in well-known people.
-Because most politicians are well-known this is a interesting knowledge base.
+\paragraph{\textbf{Freebase} (\url{https://www.freebase.com/})} This is an openly available knowledge base specialised among others in well-known people.
+Because most politicians are well-known, this is an interesting knowledge base.
 Furthermore, Freebase contains the property \textit{cause\_of\_death} which we can use to find murders or homicides among the politicians.
@@
 For this question we need also some background information. As already pointed out, DBpedia is a good source for this.
+
+\section{\hyphenpenalty=10000 \sloppy Which characteristics of a politician influence the amount of TV appearances he makes?}
+
+Politicians appear on TV quite often, but not all appear equally frequent.
+A lot of factors can influence this frequency: political party, function, statements made, previous occupations,...
+the list can go on and on.
+In this question we will research which of these characteristics actually influence the amount of such TV appearances they make.
+\par First and most importantly, we need to find how often politicians appeared on television within a certain timeframe.
+This is the \emph{response} measure.
+Next, we yet again have to build a profile for politicians, similar to that in the first question.
+Finally, we find out which features of our politician influence the response.
+
+\subsection*{Knowledge bases}
+
+In order to build the profile, we need some additional information next to the ToE knowledge base. The most important ones are those for constructing the response, e.g. the television appearances.
+
+\paragraph{BBC Programme (\url{http://www.bbc.co.uk/ontologies/po})} contains information about BBC's programmes.
+Each programme has several \texttt{Person} entities related to it trough the \emph{person} relation, so we can find out which politicians appeared when in BBC television shows.
+As it is maintained solely by the BBC, we believe it is up-to-date and accurate.
+
+\paragraph{LinkedTV (\url{http://www.linkedtv.eu/})} attempts to add meta data to television shows, split up into fragments.
+For example, it attempts to link information on all faces appearing in a fragment to a \texttt{Person}.
+This can also be useful in constructing the response measures for all politicians and even enables us to specify how long they appeared on television.
+The LinkedTV project aims at automating the process of gathering meta-data \cite{stein13}, which mean it is prone to errors in the software.
+Some of it might be corrected by hand, but we should still be careful in assuming everything is correct.
+
+\vspace{.5cm}
+\par Furthermore, we need to gather some background information from for example DBpedia or Freebase. These have already been discussed in detail, so we will not do that again.
+
+\begin{thebibliography}{9}
+
+\bibitem{stein13}
+   Daniel Stein et al.,
+  \emph{From raw data to semantically enriched hyperlinks: recent advances in the LinkedTV
+analysis workflow},
+  NEM Summit 2013,  
+  Nantes, France,
+  October 2013.
+
+\end{thebibliography}
+
 \end{document}

### 2015-11-21 exercise_6/ex6.tex
ex6.tex gemaakt
Al gestart aan rapport voor exercise 6

\documentclass[11pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{url}
\usepackage{hyperref}
\author{
  Katrien Laenen\\
  \and
  Gust Verbruggen\\
  \and
  Ward Schodts
}
\title{Knowledge \& the web: exercise session 6}
\begin{document}
\maketitle
In this report we discuss which algorithms we tried to find a good classification model that predicts if a passenger of the Titanic will survive or not.
To train the classification models, we use the information about passengers with passengerId 1 until 800 as our training data. The test data for evaluating each classification model consists of the passengers with ids 801 until 891.

\section{Rule learning}
One thing we tried was to learn classification rules from the training data.
Rule learning algorithms come with different options for several aspects of the algorithms. In the exercise session we experimented with two of these.\\
First, for choosing the conditions of a classification rule, there are two options: one is to add to the rule the condition which increases the accuracy the most, another is to add to the rule the condition which increases the information gain the most.\\
The first option resulted in the following rule set:
When evaluated on the test set, we got an accuracy of ?.
The second option resulted in this rule set:
\begin{itemize}

\item if Sex = male and Fare $\leq$ 15.173 then 0  (268 / 35)
\item if Sex = female and Fare $\textgreater$ 48.200 then 1  (4 / 76)
\item if Sex = male and Cabin = ? then 0  (0 / 0)
\item if Sex = male then 0  (152 / 62)
\item else 1  (61 / 121)

\end{itemize}
which is correct for 617 out of 779 training examples.
When evaluated on the test set, we got an accuracy of ?\\
A second aspect of rule learning is the desired pureness, which is the minimum ratio of the major class in a covered subset in order to consider the subset pure. The standard value for this is 0.9. We experimented with this value set to 0.8 and 1.
For the desired pureness set to 0.8 and the information criterion we got the following rule set:
\begin{itemize}

\item if Sex = male then 0  (420 / 97)
\item else 1  (64 / 189)

\end{itemize}
which is correct for 609 out of 770 training examples.
When evaluated on the test set, we got an accuracy of ?.
For the desired pureness set to 1 and the information gain criterion we got the following rule set:
\begin{itemize}

\item if Sex = male and Fare $\leq$ 15.173 then 0  (268 / 35)
\item if Sex = female and Fare $\textgreater$ 48.200 then 1  (4 / 76)
\item if Sex = male and Cabin = ? then 0  (0 / 0)
\item if Sex = male then 0  (152 / 62)
\item else 1  (61 / 121)

\end{itemize}
which is the same as the first rule set, which was obtained with the standard value for the desired pureness.\\
Next to these two, there are three other parameters for rule learning: sample ratio (which specifies the sample ratio of training data used for growing and pruning), minimal prune benefit (which specifies the minimum amount of benefit which must be exceeded over unpruned benefit in order to be pruned) and use local random seed (which indicates if a local random seed should be used for randomization). We did not experiment with these parameters, but kept the standard values for these, which were 0.9, 0.25 and no respectively.\\
\\
From these results we can clearly see that Sex, Fare and SibSp are features which are important for this task. That Sex and Fare were important features was to be expected. When the Titanic collided with an iceberg, women and children and people of the higher ranks were evacuated first. This is reflected in the data as we see that women and people which payed a higher fare are more likely to have survived. That the number of siblings and spouses is also an important feature can be explained as follows. People in need want to stay close to their loved ones at all costs. But how larger a group, how more difficult it was to get on a lifeboat together. As such, how more siblings and spouses someone had aboard, how less likely that person was to survive.

\section{Decision trees}

\section{?}

\end{document}

### 2015-11-21 exercise_6/ex6.tex
update ex6.tex

@@
 First, for choosing the conditions of a classification rule, there are two options: one is to add to the rule the condition which increases the accuracy the most, another is to add to the rule the condition which increases the information gain the most.\\
-The first option resulted in the following rule set:
-When evaluated on the test set, we got an accuracy of ?.
+The first option resulted in a rule set consisting of 363 rules which clearly overfitted the training data.
 The second option resulted in this rule set:

### 2015-11-22 exercise_6/ex6.tex
X-validation voorbeeld proces
added svg
Update ex6.tex
Inleiding geüpdatet

@@
-\documentclass[11pt,a4paper]{article}
+\documentclass[12pt,a4paper]{article}
 \usepackage[latin1]{inputenc}
@@
 \usepackage{amssymb}
+\usepackage{svg}
 \usepackage{url}
@@
 In this report we discuss which algorithms we tried to find a good classification model that predicts if a passenger of the Titanic will survive or not.
-To train the classification models, we use the information about passengers with passengerId 1 until 800 as our training data.
-The test data for evaluating each classification model consists of the passengers with ids 801 until 891.
+To train the classification models, we use the data in titanic_train.csv.
+Before training the models on this data, we did some preprocessing on it.
+We first removed the columns Name, Ticket and Cabin and then split the Age feature into five classes: child (0 to 9 years), teen (10 to 15 years), young (15 to 24 years), adult (25 to 59 years) and elderly (> 59 years).
+The classification models are all evaluated using cross validation.
 
@@
 
+\begin{figure}[htbp]
+  \centering
+  \includesvg[width = 0.7\textwidth]{decisiontreetitanic}
+  \caption{Decision tree with maximal depth of 3}
+\end{figure}
+
 \section{?}

### 2015-11-22 exercise_6/ex6.tex
added original decisiontree
Preprocessing seperated.

--- 2015-11-21 exercise_6/ex6.tex
@@
-\documentclass[11pt,a4paper]{article}
-\usepackage[latin1]{inputenc}
+\documentclass[12pt,a4paper]{article}
+% \usepackage[latin1]{inputenc}
 \usepackage[english]{babel}
@@
 \usepackage{amssymb}
+\usepackage{svg}
 \usepackage{url}
 \usepackage{hyperref}
+
 \author{
@@
 In this report we discuss which algorithms we tried to find a good classification model that predicts if a passenger of the Titanic will survive or not.
-To train the classification models, we use the information about passengers with passengerId 1 until 800 as our training data.
-The test data for evaluating each classification model consists of the passengers with ids 801 until 891.
+We use the data from \texttt{titanic\_train.csv} to train our model and perform cross-validation for performance assessment.
+The models used are a \textbf{rule set} and a \textbf{decision tree}.
+The rest of this document is structured as follows.
+First we describe the preprocessing steps used in order to prepare the data for better classification.
+Next, we describe the learning process for both models.
+Finally, we compare results for both learning techniques, based on the cross-validation results.
+
+\section{Preprocessing}
+In order to achieve better classification, we preprocess the data.
+This is done in two phases: feature selection to only preserve relevant features and feature engineering in the form of a discretisation step.
+
+\paragraph{Feature selection} Features that we do not think are relevant are \texttt{Name}, \texttt{Ticket}, \texttt{PassengerId}, \texttt{Embarked} and \texttt{Cabin}. They are removed.
+
+\paragraph{Discretisation} The two numerical values are discretised in accordance to some criterium.
+The \texttt{Age} feature into five age classes: child ($<$ 9 years), teen (10 to 15 years), young (15 to 24 years), adult (25 to 59 years) and elderly ($>$ 59 years).
+To discretise \texttt{Fare}, we take a look at a histogram plot, as seen in Figure~\ref{fig:histfare}.
+There are a lot more low fares.
+The three leftmost bars get their own bin.
+The chosen discretisation is: 0-10, 10-20, 20-30, 30-100 and 100+.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width = .7\textwidth]{fare_histogram.pdf}
+	\caption{Histogram for the \texttt{Fare} feature}
+	\label{fig:histfare}
+\end{figure}
 
 \section{Rule learning}
-One thing we tried was to learn classification rules from the training data.
-Rule learning algorithms come with different options for several aspects of the algorithms. In the exercise session we experimented with two of these.\\
-First, for choosing the conditions of a classification rule, there are two options: one is to add to the rule the condition which increases the accuracy the most, another is to add to the rule the condition which increases the information gain the most.\\
+One model we tried was to learn classification rules from the training data.
+Rule learning algorithms come with different options for several aspects of the algorithms.
+In the exercise session we experimented with two of these.
+\par First, for choosing the conditions of a classification rule, there are two options: one is to add to the rule the condition which increases the accuracy the most, another is to add to the rule the condition which increases the information gain the most.
 The first option resulted in a rule set consisting of 363 rules which clearly overfitted the training data.
@@
 
+%\begin{figure}[htbp]
+%  \centering
+%  \includesvg[width = 0.7\textwidth]{decisiontreetitanic}
+%  \caption{Decision tree with maximal depth of 3}
+%\end{figure}
+
 \section{?}

### 2015-11-22 exercise_6/ex6.tex
decision tree

--- 2015-11-21 exercise_6/ex6.tex
@@
 \usepackage{amssymb}
+\usepackage{svg}
+\usepackage{float}
 \usepackage{url}
@@
 \section{Decision trees}
+Apart from \emph{rule learning} we also experimented witch decision trees.
+First we applied the standard decision tree in RapidMiner, it created a to complicated decision tree, as you can see in figure 1.
+\begin{figure}[H]
+  \centering
+  \includesvg[width = 1.5\textwidth]{decisiontreetitanic_original}
+  \caption{Original decision tree with maximal depth of 20}
+\end{figure}
+Next we limited the maximal depth of the decision tree to 3. This gave us figure 2, which is much more usefull.
+\begin{figure}[H]
+  \centering
+  \includesvg[width = 1\textwidth]{decisiontreetitanic}
+  \caption{Decision tree with maximal depth of 3}
+\end{figure}
 

### 2015-11-22 exercise_6/ex6.tex

--- 2015-11-22 exercise_6/ex6.tex
@@
 \usepackage{svg}
+\usepackage{float}
 \usepackage{url}
@@
 In this report we discuss which algorithms we tried to find a good classification model that predicts if a passenger of the Titanic will survive or not.
+
 We use the data from \texttt{titanic\_train.csv} to train our model and perform cross-validation for performance assessment.
@@
 
-%\begin{figure}[htbp]
-%  \centering
-%  \includesvg[width = 0.7\textwidth]{decisiontreetitanic}
-%  \caption{Decision tree with maximal depth of 3}
-%\end{figure}
+Apart from \emph{rule learning} we also experimented witch decision trees.
+First we applied the standard decision tree in RapidMiner, it created a too complicated decision tree, as you can see in figure 1.
+\begin{figure}[H]
+  \centering
+  \includesvg[width = 1.5\textwidth]{decisiontreetitanic_original}
+  \caption{Original decision tree with maximal depth of 20}
+\end{figure}
+Next we limited the maximal depth of the decision tree to 3. This gave us figure 2, which is much more usefull.
+\begin{figure}[H]
+  \centering
+  \includesvg[width = 1\textwidth]{decisiontreetitanic}
+  \caption{Decision tree with maximal depth of 3}
+\end{figure}
 

### 2015-11-22 exercise_6/ex6.tex
added tabular
Update ex6.tex

--- 2015-11-22 exercise_6/ex6.tex
@@
 \section{Rule learning}
-One model we tried was to learn classification rules from the training data.
-Rule learning algorithms come with different options for several aspects of the algorithms.
-In the exercise session we experimented with two of these.
-\par First, for choosing the conditions of a classification rule, there are two options: one is to add to the rule the condition which increases the accuracy the most, another is to add to the rule the condition which increases the information gain the most.
-The first option resulted in a rule set consisting of 363 rules which clearly overfitted the training data.
-The second option resulted in this rule set:
+One thing we tried was to learn classification rules from the training data.
+Rule learning algorithms come with different options for several aspects of the algorithms. In the exercise session we experimented with two of these.\\
+First, for choosing the conditions of a classification rule, there are two options: one is to add to the rule the condition which increases the accuracy the most, another is to add to the rule the condition which increases the information gain the most.\\
+The accuracy criterion option resulted in the following rule set:
 \begin{itemize}
 
-\item if Sex = male and Fare $\leq$ 15.173 then 0  (268 / 35)
-\item if Sex = female and Fare $\textgreater$ 48.200 then 1  (4 / 76)
-\item if Sex = male and Cabin = ? then 0  (0 / 0)
-\item if Sex = male then 0  (152 / 62)
-\item else 1  (61 / 121)
+\item if Parch > 5.500 then 0  (1 / 0)
+\item if Fare = >10 and Sex = male then 0  (170 / 25)
+\item if Sex = female then 1  (63 / 197)
+\item else 0  (171 / 61)
 
 \end{itemize}
-which is correct for 617 out of 779 training examples.
-When evaluated on the test set, we got an accuracy of ?\\
+%which is correct for 539 out of 688 training examples.
+The information gain criterion option resulted in this rule set:
+\begin{itemize}
+
+\item if Sex = male and Fare = >10 then 0  (170 / 25)
+\item if Sex = female then 1  (64 / 197)
+\item if Fare = 10-20 and Parch ≤ 0.500 then 0  (66 / 7)
+\item else 0  (111 / 54)
+
+\end{itemize}
+%which is correct for 544 out of 694 training examples.
 A second aspect of rule learning is the desired pureness, which is the minimum ratio of the major class in a covered subset in order to consider the subset pure.
@@
 We experimented with this value set to 0.8 and 1.
-For the desired pureness set to 0.8 and the information criterion we got the following rule set:
+For the desired pureness set to 0.8 and the accuracy criterion we got the following rule set:
 \begin{itemize}
 
-\item if Sex = male then 0  (420 / 97)
-\item else 1  (64 / 189)
+\item if Parch > 5.500 then 0  (1 / 0)
+\item if Fare = >10 then 0  (189 / 47)
+\item if Sex = female then 1  (44 / 175)
+\item else 0  (171 / 61)
 
 \end{itemize}
-which is correct for 609 out of 770 training examples.
-When evaluated on the test set, we got an accuracy of ?.
-For the desired pureness set to 1 and the information gain criterion we got the following rule set:
+%which is correct for 536 out of 688 training examples.
+This rule set is very similar to the rule set obtained with the accuracy criterion option and desired pureness of 0.9.
+The only difference is that in the second rule the \textit{Sex = male} condition now disappeared from the condition part.
+For the desired pureness set to 0.8 and the information gain criterion we got the following rule set:
 \begin{itemize}
 
-\item if Sex = male and Fare $\leq$ 15.173 then 0  (268 / 35)
-\item if Sex = female and Fare $\textgreater$ 48.200 then 1  (4 / 76)
-\item if Sex = male and Cabin = ? then 0  (0 / 0)
-\item if Sex = male then 0  (152 / 62)
-\item else 1  (61 / 121)
+\item if Sex = male then 0  (360 / 93)
+\item else 1  (57 / 177)
 
 \end{itemize}
-which is the same as the first rule set, which was obtained with the standard value for the desired pureness.\\
-Next to these two, there are three other parameters for rule learning: sample ratio (which specifies the sample ratio of training data used for growing and pruning), minimal prune benefit (which specifies the minimum amount of benefit which must be exceeded over unpruned benefit in order to be pruned) and use local random seed (which indicates if a local random seed should be used for randomization).
+%which is correct for 537 out of 687 training examples.
+When comparing this rule set with the rule set obtained for the information gain criterion with the desired pureness set to 0.9, we see that this rule set is a great simplification of the other.
+For the desired pureness set to 1 and the accuracy criterion we got exactly the same rule set as when setting the desired pureness to 0.9 for that criterion.
+The same happened for the desired pureness set to 1 and the information gain criterion, which also resulted in the same rule set as when setting the pureness to 0.9 and keeping the information criterion.\\
+Next to the criterion and desired pureness, there are three other parameters for rule learning: sample ratio (which specifies the sample ratio of training data used for growing and pruning), minimal prune benefit (which specifies the minimum amount of benefit which must be exceeded over unpruned benefit in order to be pruned) and use local random seed (which indicates if a local random seed should be used for randomization).
 We did not experiment with these parameters, but kept the standard values for these, which were 0.9, 0.25 and no respectively.\\
 \\
-From these results we can clearly see that Sex, Fare and SibSp are features which are important for this task.
+From these results we can clearly see that Sex, Fare and Parch are features which are important for this task.
 That Sex and Fare were important features was to be expected.
@@
 This is reflected in the data as we see that women and people which payed a higher fare are more likely to have survived.
-That the number of siblings and spouses is also an important feature can be explained as follows.
+That the number of parents and children is also an important feature can be explained as follows.
 People in need want to stay close to their loved ones at all costs.
 But how larger a group, how more difficult it was to get on a lifeboat together.
-As such, how more siblings and spouses someone had aboard, how less likely that person was to survive.
+Also, little children and old people need much more assistence to even reach a lifeboat.
+As such, how more children and parents someone had aboard, how less likely that person was to survive.
 

### 2015-11-22 exercise_6/ex6.tex

@@
 
-%\begin{figure}[htbp]
-%  \centering
-%  \includesvg[width = 0.7\textwidth]{decisiontreetitanic}
-%  \caption{Decision tree with maximal depth of 3}
-%\end{figure}
+Apart from \emph{rule learning} we also experimented witch decision trees.
+First we applied the standard decision tree in RapidMiner, it created a too complicated decision tree, as you can see in figure 1.
+\begin{figure}[H]
+  \centering
+  \includesvg[width = 1.5\textwidth]{decisiontreetitanic_original}
+  \caption{Original decision tree with maximal depth of 20}
+\end{figure}
+Next we limited the maximal depth of the decision tree to 3. This gave us figure 2, which is much more usefull.
+\begin{figure}[H]
+  \centering
+  \includesvg[width = 1\textwidth]{decisiontreetitanic}
+  \caption{Decision tree with maximal depth of 3}
+\end{figure}
 
-\section{?}
+\section{Rule learning vs. Decision trees}
+
+Settings for Rule learning 1:
+\begin{itemize}
+\item ...
+\end{itemize}
+
+Settings for Rule learning 2:
+\begin{itemize}
+\item ...
+\end{itemize}
+
+Settings for Decision tree 1:
+\begin{itemize}
+\item ...
+\end{itemize}
+
+Settings for Decision tree 2:
+\begin{itemize}
+\item ...
+\end{itemize}
+
+\begin{figure}[H]
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline 
+• & Precision & Accuracy & Recall\\ 
+\hline 
+Rule learning 1 & • & • & • \\ 
+\hline 
+Rule learning 2 & • & • & • \\ 
+\hline 
+Decision tree 1 & • & • & • \\ 
+\hline 
+Decision tree 2 & • & • & • \\ 
+\hline 
+\end{tabular} 
+\caption{Overview}
+\end{figure}
 

### 2015-11-22 exercise_6/ex6.tex
Fixed operators

@@
 One thing we tried was to learn classification rules from the training data.
-Rule learning algorithms come with different options for several aspects of the algorithms. In the exercise session we experimented with two of these.\\
-First, for choosing the conditions of a classification rule, there are two options: one is to add to the rule the condition which increases the accuracy the most, another is to add to the rule the condition which increases the information gain the most.\\
+Rule learning algorithms come with different options for several aspects of the algorithms.
+In the exercise session we experimented with two of these.
+\par First, for choosing the conditions of a classification rule, there are two options: one is to add to the rule the condition which increases the accuracy the most, another is to add to the rule the condition which increases the information gain the most.
 The accuracy criterion option resulted in the following rule set:
@@
 
-\item if Parch > 5.500 then 0  (1 / 0)
-\item if Fare = >10 and Sex = male then 0  (170 / 25)
+\item if Parch $>$ 5.500 then 0  (1 / 0)
+\item if Fare $\geq$ 10 and Sex = male then 0  (170 / 25)
 \item if Sex = female then 1  (63 / 197)
@@
 
-\item if Sex = male and Fare = >10 then 0  (170 / 25)
+\item if Sex = male and Fare $\geq$ 10 then 0  (170 / 25)
 \item if Sex = female then 1  (64 / 197)
-\item if Fare = 10-20 and Parch ≤ 0.500 then 0  (66 / 7)
+\item if Fare = 10-20 and Parch $\leq$ 0.500 then 0  (66 / 7)
 \item else 0  (111 / 54)
@@
 
-\item if Parch > 5.500 then 0  (1 / 0)
-\item if Fare = >10 then 0  (189 / 47)
+\item if Parch $>$ 5.500 then 0  (1 / 0)
+\item if Fare $\geq$ 10 then 0  (189 / 47)
 \item if Sex = female then 1  (44 / 175)
@@
 
-Apart from \emph{rule learning} we also experimented witch decision trees.
+Apart from rule set learning, we also experimented witch decision trees.
 First we applied the standard decision tree in RapidMiner, it created a too complicated decision tree, as you can see in figure 1.
+
 \begin{figure}[H]
   \centering
-  \includesvg[width = 1.5\textwidth]{decisiontreetitanic_original}
+  \includegraphics[width = 1.5\textwidth]{decisiontreetitanic_original.pdf}
   \caption{Original decision tree with maximal depth of 20}
@@
   \centering
-  \includesvg[width = 1\textwidth]{decisiontreetitanic}
+  \includegraphics[width = 1\textwidth]{decisiontreetitanic.pdf}
   \caption{Decision tree with maximal depth of 3}

### 2015-11-22 exercise_6/ex6.tex
Decision tree part added

@@
 Apart from rule set learning, we also experimented witch decision trees.
-First we applied the standard decision tree in RapidMiner, it created a too complicated decision tree, as you can see in figure 1.
+Since we are working with a mix of nominal and numeric data, this is a suitable model, because each node can use its own \emph{rule} for splitting on an attribute.
+We will describe how we tweaked the learning parameters in order to achieve better results.
+The initial tree is shown in Figure~\ref{fig:tree_initial}.
 
-\begin{figure}[H]
+\begin{figure}[htbp]
   \centering
-  \includegraphics[width = 1.5\textwidth]{decisiontreetitanic_original.pdf}
-  \caption{Original decision tree with maximal depth of 20}
+  \includegraphics[width = .6\textwidth]{tree_initial}
+  \captionsetup{width=.8\textwidth}
+  \caption{Tree learned with default parameters}
+  \label{fig:tree_initial}
 \end{figure}
-Next we limited the maximal depth of the decision tree to 3. This gave us figure 2, which is much more usefull.
-\begin{figure}[H]
+
+\par The most obvious observation about this initial model is that female passengers with third class tickets are not yet classified very accurately, yet the tree did not split on it.
+In order to improve on this, we can adjust the splitting criterion to \emph{accuracy}.
+It will split nodes such that the accuracy of the tree increases.
+This results in a very sparse and large tree, which is not shown for exactly that reason.
+By changing the maximal depth of the tree, we can prevent it from getting too large.
+A maximal depth of 4 was found to provide good results.
+The result is shown in Figure~\ref{fig:tree_accuracy}.
+\begin{figure}[htbp]
   \centering
-  \includegraphics[width = 1\textwidth]{decisiontreetitanic.pdf}
-  \caption{Decision tree with maximal depth of 3}
+  \includegraphics[width = .6\textwidth]{tree_accuracy}
+  \captionsetup{width=.8\textwidth}
+  \caption{Tree learned with \emph{accuracy} splitting criterion and maximum depth of 4.}
+  \label{fig:tree_accuracy}
 \end{figure}
+As we can see, this achieved the desired result of splitting the undecided node in four new nodes, three of which perform clearly better.
+The final step is improving prediction for males.
+While its accuracy is quite high, the recall for surviving males is zero.
+This probably happens because the gain in criterion is not sufficiently high for the pre-pruning step to split the node.
+By lowering the minimum gain during pre-pruning, we enable the algorithm to split easier on nodes.
+Because the \texttt{Fare} node is already split until max depth, we expect that only the rightmost node (males) will be further split by this setting.
+Figure~\ref{fig:tree_final} confirms this assumption and shows the final model.
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width = .8\textwidth]{tree_final}
+  \captionsetup{width=.8\textwidth}
+  \caption{Tree learned with \emph{accuracy} splitting criterion, maximum depth of 4 and minimum information gain of 0.01.}
+  \label{fig:tree_final}
+\end{figure}
+\par This model is pretty intuitive.
+For females, class is the most important deciding factor.
+Amongst the lowest class women, the ones that payed most for their ticket surprisingly have the lowest survival rate.
+For males, age is the most important deciding factor.
+Children have a far higher survival rate than men.
 

### 2015-11-22 exercise_6/ex6.tex
Update ex6.tex
Paar schrijffoutjes verbeterd

@@
 
-Apart from rule set learning, we also experimented witch decision trees.
+Apart from rule set learning, we also experimented with decision trees.
 Since we are working with a mix of nominal and numeric data, this is a suitable model, because each node can use its own \emph{rule} for splitting on an attribute.
@@
 \par This model is pretty intuitive.
-For females, class is the most important deciding factor.
+For females, Class is the most important deciding factor.
 Amongst the lowest class women, the ones that payed most for their ticket surprisingly have the lowest survival rate.
-For males, age is the most important deciding factor.
+For males, Age is the most important deciding factor.
 Children have a far higher survival rate than men.

### 2015-11-22 exercise_6/ex6.tex
Process

@@
 %which is correct for 544 out of 694 training examples.
-A second aspect of rule learning is the desired pureness, which is the minimum ratio of the major class in a covered subset in order to consider the subset pure.
+\par A second aspect of rule learning is the desired pureness, which is the minimum ratio of the major class in a covered subset in order to consider the subset pure.
 The standard value for this is 0.9.
@@
 \begin{itemize}
-
 \item if Parch $>$ 5.500 then 0  (1 / 0)
@@
 \item else 0 (171 / 61)
-
 \end{itemize}
 %which is correct for 536 out of 688 training examples.
-This rule set is very similar to the rule set obtained with the accuracy criterion option and desired pureness of 0.9.
+\par This rule set is very similar to the rule set obtained with the accuracy criterion option and desired pureness of 0.9.
 The only difference is that in the second rule the \textit{Sex = male} condition now disappeared from the condition part.
@@
 %which is correct for 537 out of 687 training examples.
-When comparing this rule set with the rule set obtained for the information gain criterion with the desired pureness set to 0.9, we see that this rule set is a great simplification of the other.
+\par When comparing this rule set with the rule set obtained for the information gain criterion with the desired pureness set to 0.9, we see that this rule set is a great simplification of the other.
 For the desired pureness set to 1 and the accuracy criterion we got exactly the same rule set as when setting the desired pureness to 0.9 for that criterion.
-The same happened for the desired pureness set to 1 and the information gain criterion, which also resulted in the same rule set as when setting the pureness to 0.9 and keeping the information criterion.\\
-Next to the criterion and desired pureness, there are three other parameters for rule learning: sample ratio (which specifies the sample ratio of training data used for growing and pruning), minimal prune benefit (which specifies the minimum amount of benefit which must be exceeded over unpruned benefit in order to be pruned) and use local random seed (which indicates if a local random seed should be used for randomization).
-We did not experiment with these parameters, but kept the standard values for these, which were 0.9, 0.25 and no respectively.\\
-\\
-From these results we can clearly see that Sex, Fare and Parch are features which are important for this task.
+The same happened for the desired pureness set to 1 and the information gain criterion, which also resulted in the same rule set as when setting the pureness to 0.9 and keeping the information criterion.
+\par Next to the criterion and desired pureness, there are three other parameters for rule learning: sample ratio (which specifies the sample ratio of training data used for growing and pruning), minimal prune benefit (which specifies the minimum amount of benefit which must be exceeded over unpruned benefit in order to be pruned) and use local random seed (which indicates if a local random seed should be used for randomization).
+We did not experiment with these parameters, but kept the standard values for these, which were 0.9, 0.25 and no respectively.
+\par From these results we can clearly see that Sex, Fare and Parch are features which are important for this task.
 That Sex and Fare were important features was to be expected.

### 2015-11-22 exercise_6/ex6.tex
laatste

@@
 Children have a far higher survival rate than men.
-
+\pagebreak
 \section{Rule learning vs. Decision trees}
 
-Settings for Rule learning 1:
-\begin{itemize}
-\item ...
-\end{itemize}
-
-Settings for Rule learning 2:
-\begin{itemize}
-\item ...
-\end{itemize}
-
-Settings for Decision tree 1:
-\begin{itemize}
-\item ...
-\end{itemize}
-
-Settings for Decision tree 2:
-\begin{itemize}
-\item ...
-\end{itemize}
-
-\begin{figure}[H]
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline 
-• & Precision & Accuracy & Recall\\ 
-\hline 
-Rule learning 1 & • & • & • \\ 
-\hline 
-Rule learning 2 & • & • & • \\ 
-\hline 
-Decision tree 1 & • & • & • \\ 
-\hline 
-Decision tree 2 & • & • & • \\ 
-\hline 
-\end{tabular} 
-\caption{Overview}
-\end{figure}
+We conclude this report with a brief summary of our results and our conclusion about the methods.
+In following table we give the accuracy, precision and recall of our best configuration.
+With \emph{accuracy} we mean the retrieved instances 
+From these scores we decided what was in our opinion the best method.
 

### 2015-11-22 exercise_6/ex6.tex
accuracy

@@
 In following table we give the accuracy, precision and recall of our best configuration.
-With \emph{accuracy} we mean the retrieved instances 
+With \emph{accuracy} we mean the proportion of true results (both true positives and true negatives) among the total number of cases examined.
+For the Titanic case this would mean:
+$$accuracy = \frac{\#\text{true dead} + \#\text{true alive} }{\#\text{true dead} + \#\text{false dead} + \#\text{true alive} + \#\text{false alive}}$$
 From these scores we decided what was in our opinion the best method.

### 2015-11-22 exercise_6/ex6.tex
precision

@@
 We conclude this report with a brief summary of our results and our conclusion about the methods.
-In following table we give the accuracy, precision and recall of our best configuration.
+To decide if either Rule learning is better than Decision trees we look at three performance measures, namely: \textbf{accuracy}, \textbf{precision} and \textbf{recall}.
+
 With \emph{accuracy} we mean the proportion of true results (both true positives and true negatives) among the total number of cases examined.
@@
 $$accuracy = \frac{\#\text{true dead} + \#\text{true alive} }{\#\text{true dead} + \#\text{false dead} + \#\text{true alive} + \#\text{false alive}}$$
+
+\emph{Precision} is the fraction of retrieved instances that are relevant:
+$$precision = \frac{\#\text{true alive}}{\#\text{true alive} + \#\text{false alive}}$$
+\\
+\\
+In following table we give the accuracy, precision and recall of our best configuration.
 From these scores we decided what was in our opinion the best method.

### 2015-11-22 exercise_6/ex6.tex
conclusion

@@
-\documentclass[12pt,a4paper]{article}
+\documentclass[11pt,a4paper]{article}
 % \usepackage[latin1]{inputenc}
@@
 Children have a far higher survival rate than men.
-\pagebreak
+
 \section{Rule learning vs. Decision trees}
@@
 $$precision = \frac{\#\text{true alive}}{\#\text{true alive} + \#\text{false alive}}$$
+
+Finally \emph{recall} (or sensitivity) is the fraction of relevant instances that are retrieved:
+$$recall = \frac{\#\text{true alive}}{\#\text{true alive} + \#\text{false dead}}$$
 \\
 \\
-In following table we give the accuracy, precision and recall of our best configuration.
-From these scores we decided what was in our opinion the best method.
+In following table we give the accuracy, precision and recall of our best configuration from both rule learning and decision trees.
+With best we mean the highest \textbf{accuracy}, \textbf{precision} and \textbf{recall}.
+\begin{figure}[H]
+\centering
+\begin{tabular}{c|c|c|c}
+
+• & Accuracy & Precision & Recall \\ 
+\hline 
+Rule learning & 78.78\% & 75.95\% & 66.39\% \\ 
+\hline 
+Decision trees & 81.46\% & 81.37\% & 71.26\% \\
+
+\end{tabular} 
+\caption{Our results}
+\end{figure}
+From these scores it is obvious to see that the clustering with a decision tree is a lot better. With our configurations decision trees outperforms rule learning in every performance measure.
 

### 2015-11-25 exercise_6/ex6.tex
conclusion
ex7

@@
 \hline 
-Rule learning & 78.78\% & 75.95\% & 66.39\% \\ 
+Rule learning & 78.99\% & 80.59\% & 65.87\% \\ 
 \hline 
@@
 From these scores it is obvious to see that the clustering with a decision tree is a lot better. With our configurations decision trees outperforms rule learning in every performance measure.
+\\
+\\
+We can conclude that a \textbf{decision tree} works better in this specific case.
+\pagebreak
+\section{Further experiments with evaluation methods}
 
+In our previous evaluations we used the regular cross-validation.
+For session 7 we experimented with \textit{leave\_one\_out} cross-validation (this is just a setting in RapidMiner).
+Actually it's going to leave out one example of the training set.
+This example is used to test the model that is build, using all the other examples.
+This is done for every element in the dataset.
+This way, this is very computational expensive.
+\\
+\\
+Apart from leave\_one\_out we experimented with \textit{split validation}.
+This method splits the data at random in a training part and a test part.
+One can specify the ratio test/training data in RapidMiner.
+We used the standard value here: 0.7.
+
+In the following tables we give a short summary of our results on the best model from the previous section.
+
+\begin{figure}[H]
+\centering
+\begin{tabular}{c|c|c|c}
+
+• & Accuracy & Precision & Recall \\ 
+\hline 
+Cross-validation & 78.99\% & 80.59\% & 65.87\% \\ 
+\hline 
+leave\_one\_out & 78.01\% & 75.09\% & 68.62\% \\ 
+\hline 
+Split validation & 76.64\% & 75.00\% & 62.79\% \\
+
+\end{tabular} 
+\caption{Results for Rule Learning}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\begin{tabular}{c|c|c|c}
+
+• & Accuracy & Precision & Recall \\ 
+\hline 
+Cross-validation & 81.46\% & 81.37\% & 71.26\% \\ 
+\hline 
+leave\_one\_out & 82.47\% &82.35\% & 72.66\% \\ 
+\hline 
+Split validation & 82.46\% & 82.35\% & 72.66\% \\
+
+\end{tabular} 
+\caption{Results for Decision Trees}
+\end{figure}
+
+We can conlude that the new evaluation methods give worse results for the rule learning approach. In contrary the results for decision trees became even better. 
 \end{document}

### 2015-12-08 project/queries/runqueries.pl
Got nobelprize without links :)

@@ -1,5 +1,5 @@
 #!/usr/bin/perl
 
-$result = `rsparql --query=allnobelwinners.rq --service=http://data.nobelprize.org/sparql --results=csv`;
+$result = `rsparql --query=allnobelwinners.rq --service=http://data.nobelprize.org/sparql --results=csv >> test.csv`;
 
 print $result;

### 2015-12-08 project/queries/runqueries.pl
group because bad distinct query

@@ -1,5 +1,5 @@
 #!/usr/bin/perl
 
-$result = `rsparql --query=allnobelwinners.rq --service=http://data.nobelprize.org/sparql --results=csv >> test.csv`;
+$result = `rsparql --query=allnobelwinners.rq --service=http://data.nobelprize.org/sparql --results=csv`;
 
 print $result;

### 2015-12-09 project/scripts/getRankings.pl
no message

@@ -1,0 +1,39 @@
+#!/usr/bin/perl
+
+use LWP::Simple qw(get);
+
+($out) = @ARGV;
+if (not defined $out) {
+	$out = 'rankings.csv';
+}
+
+$html = get "http://www.shanghairanking.com/ARWU2015.html";
+
+# Parse table
+$th = 'name="UniversityRanking">';
+$tf = '<\/table>';
+$html =~ /$th(.+)$tf/s;
+$table = $1;
+
+# Parse rows
+@rows = $table =~  /class="bgf[5d]">(.*?)<tr/g;
+
+open $f, '>', $out;
+foreach $r (@rows) {
+
+	# Parse cells
+	@cells = $r =~ /<td.*?>(.*?)<\/td>/g;
+
+	# Get university name
+	$cells[1] =~ /<a.*?>(.*?)<\/a>/;
+	$name = $1;
+
+	# Get award score
+	$cells[6] =~ /<div>(.*?)\s<\/div>/;
+	$score = $1;
+
+	# Write to file
+	print $f "$name,$score\n";
+
+}
+close $f;

### 2015-12-09 project/scripts/getRankings.pl
Typos

@@ -33,7 +33,7 @@ foreach $r (@rows) {
 	$score = $1;
 
 	# Write to file
-	print $f "$name,$score\n";
+	print $f "$name;$score\n";
 
 }
 close $f;

### 2015-12-10 project/scripts/getRankings.pl
Number of speeches and Scholar ranking.

@@ -4,7 +4,9 @@ use LWP::Simple qw(get);
 
 ($out) = @ARGV;
 if (not defined $out) {
-	$out = 'rankings.csv';
+	$out = "../data/rankings.csv";
+} else {
+	$out = "../data/$out.csv";
 }
 
 $html = get "http://www.shanghairanking.com/ARWU2015.html";

### 2015-12-10 project/scripts/getScholarRanking.pl

@@ -1,0 +1,27 @@
+#!/usr/bin/perl
+
+use LWP::UserAgent;
+use URI;
+
+($name) = @ARGV;
+if (not defined $name) {
+  die "No name given\n";
+}
+
+# Build URI
+$url = URI->new('http://scholar.google.be/scholar');
+$url->query_form(
+  "hl" => "nl",
+  "q"  => "author:$name"
+);
+
+# Initialize user agent
+$ua = LWP::UserAgent->new;
+$ua->timeout(10);
+$ua->agent("Mozilla/5.0");
+
+# Get content and parse number of results
+$html = $ua->get($url);
+$html->content() =~ /Ongeveer\s(.+?)\sresultaten/;
+
+print $1;

### 2015-12-14 project/src/Main.java
ToE politiekers

@@ -3,119 +3,78 @@ import org.apache.jena.rdf.model.Model;
 import org.apache.jena.rdf.model.ModelFactory;
 
 import java.io.*;
+import java.nio.charset.Charset;
+import java.nio.file.Files;
+import java.nio.file.Paths;
+import java.util.ArrayList;
+import java.util.List;
+import java.util.stream.Collector;
+import java.util.stream.Collectors;
 
 public class Main {
 
+    private List<String> strings = new ArrayList<>();
+
     public static void main(String[] args) throws IOException {
-        test2();
+        outerQuery();
     }
 
-    private void test1() throws IOException {
-        // Open the bloggers RDF graph from the filesystem
-        InputStream in = null;
-        try {
-            in = new FileInputStream(new File("bloggers.rdf"));
-        } catch (FileNotFoundException e) {
-            e.printStackTrace();
-        }
-        // Create an empty in-memory model and populate it from the graph
-        Model model = ModelFactory.createMemModelMaker().createModel("test");
-        model.read(in, null); // null base URI, since model URIs are absolute
-        in.close();
-        // Create a new query
-        String queryString =
-                "PREFIX foaf: <http://xmlns.com/foaf/0.1/> " +
-                        "SELECT ?url " +
-                        "WHERE {" +
-                        " ?contributor foaf:name \"Jon Foobar\" . " +
-                        " ?contributor foaf:weblog ?url . " +
-                        " }";
+    private static void outerQuery() throws IOException {
+        String queryString = readFile(System.getProperty("user.dir") + "/queries/ToEpoliticians.rq", Charset.defaultCharset());
         Query query = QueryFactory.create(queryString);
-        // Execute the query and obtain results
-        QueryExecution qe = QueryExecutionFactory.create(query, model);
-        ResultSet results = qe.execSelect();
-        // Output query results
-        ResultSetFormatter.out(System.out, results, query);
-        // Important - free up resources used running the query
-        qe.close();
-    }
-
-    private static  void test2() {
-        String queryString=
-        "PREFIX dbpedia-owl: <http://dbpedia.org/ontology/>"+
-        "PREFIX nobel: <http://data.nobelprize.org/terms/>"+
-        "PREFIX foaf: <http://xmlns.com/foaf/0.1/>"+
-        "PREFIX yago: <http://yago-knowledge.org/resource/>"+
-        "PREFIX viaf: <http://viaf.org/viaf/>"+
[…]

### 2015-12-16 project/scripts/getScholarRanking.pl
finally all data

@@ -1,4 +1,4 @@
-#!/usr/bin/perl
+  #!/usr/bin/perl
 
 use LWP::UserAgent;
 use URI;

### 2015-12-16 project/src/Main.java

@@ -1,12 +1,14 @@
 import org.apache.jena.query.*;
 import org.apache.jena.rdf.model.Model;
 import org.apache.jena.rdf.model.ModelFactory;
+import org.apache.jena.rdf.model.RDFNode;
 
 import java.io.*;
 import java.nio.charset.Charset;
 import java.nio.file.Files;
 import java.nio.file.Paths;
 import java.util.ArrayList;
+import java.util.HashSet;
 import java.util.List;
 import java.util.stream.Collector;
 import java.util.stream.Collectors;
@@ -15,24 +17,58 @@ public class Main {
 
     private List<String> strings = new ArrayList<>();
 
-    public static void main(String[] args) throws IOException {
-        outerQuery();
+    public static void main(String[] args) throws Exception {
+
+//        outerQuery();
+//        dbPedia("scientist.rq");
+//        dbPedia("politician.rq");
+//        dbPedia("economist.rq");
+//        dbPedia("writer.rq");
+        uniques("data.csv");
     }
 
-    private static void outerQuery() throws IOException {
-        String queryString = readFile(System.getProperty("user.dir") + "/queries/ToEpoliticians.rq", Charset.defaultCharset());
+    private static void dbPedia(String queryFile) throws IOException {
+        String queryString = readFile(System.getProperty("user.dir") + "/queries/" + queryFile);
         Query query = QueryFactory.create(queryString);
-        QueryExecution qexec = QueryExecutionFactory.sparqlService("http://linkedpolitics.ops.few.vu.nl/sparql/", query);
+        QueryExecution qexec = QueryExecutionFactory.sparqlService("http://dbpedia.org/sparql/", query);
 
         try {
             ResultSet results = qexec.execSelect();
 
+
+            for (; results.hasNext(); ) {
+                QuerySolution solution = results.nextSolution();
+                System.out.println(solution);
+                List<String> res = results.getResultVars().stream().map(rv -> getSolutionLiteral(solution, rv)).collect(Collectors.toList());
+                writeToCSV(res, "data.csv");
+                System.out.println(solution);
+            }
+
+
+        } finally {
+            qexec.close();
+        }
+    }
+
+    private static void outerQuery() throws IOException {
+        String queryString = readFile(System.getProperty("user.dir") + "/queries/ToEpoliticians.rq");
+        Query query = QueryFactory.create(queryString);
[…]

### 2015-12-16 project/src/Main.java
some error

@@ -19,11 +19,11 @@ public class Main {
 
     public static void main(String[] args) throws Exception {
 
-//        outerQuery();
-//        dbPedia("scientist.rq");
-//        dbPedia("politician.rq");
-//        dbPedia("economist.rq");
-//        dbPedia("writer.rq");
+        outerQuery();
+        dbPedia("scientist.rq");
+        dbPedia("politician.rq");
+        dbPedia("economist.rq");
+        dbPedia("writer.rq");
         uniques("data.csv");
     }
 

### 2015-12-16 project/src/Main.java
presentatie

@@ -19,7 +19,7 @@ public class Main {
 
     public static void main(String[] args) throws Exception {
 
-        outerQuery();
+        //outerQuery();
         dbPedia("scientist.rq");
         dbPedia("politician.rq");
         dbPedia("economist.rq");

### 2015-12-16 project/scripts/getUniversityRanking.pl
Data schema's

@@ -1,0 +1,35 @@
+#!/usr/bin/perl
+
+use Text::PhraseDistance qw(pdistance);
+use Text::Levenshtein qw(distance);
+
+($university) = @ARGV;
+if (not defined $university) {
+	die "No university given\n";
+}
+
+# Read the ranking file
+$rankingFile = "../data/rankings.csv";
+if (not -e $rankingFile) {
+  `perl getRankings.pl rankings`;
+}
+open $f, '<', $rankingFile;
+
+# Parse university scores
+%universityScores;
+while(<$f>) {
+  @u = split /;/, $_;
+  $universityScores{$u[0]} = $u[1];
+}
+
+$set = "abcdefghijklmnopqrstuvwxyz";
+$set .= uc $set;
+
+%universityDistances;
+foreach $u (keys %universityScores) {
+  $universityDistances{$u} = pdistance($university, $u, $set, \&distance);
+}
+
+foreach $name (sort { $universityDistances{$a} <=> $universityDistances{$b} } keys %universityDistances) {
+    printf "%-8s %s\n", $name, $universityDistances{$name};
+}

### 2015-12-16 project/src/Main.java
prizes

@@ -99,7 +99,7 @@ public class Main {
 
     }
 
-    private static String getSolutionLiteral(QuerySolution solution, String rv) {
+    public static String getSolutionLiteral(QuerySolution solution, String rv) {
         try {
             return solution.getLiteral(rv).getValue().toString();
         } catch (NullPointerException e) {
@@ -107,7 +107,7 @@ public class Main {
         }
     }
 
-    private static List<String> readLines(String path) throws IOException {
+    public static List<String> readLines(String path) throws IOException {
         return Files.readAllLines(Paths.get(path), Charset.defaultCharset());
 
     }
@@ -118,14 +118,14 @@ public class Main {
     }
 
 
-    private static String readFile(String path)
+    public static String readFile(String path)
             throws IOException {
         byte[] encoded = Files.readAllBytes(Paths.get(path));
         return new String(encoded, Charset.defaultCharset());
     }
 
 
-    private static void writeToCSV(List<String> strings, String fileName) {
+    public static void writeToCSV(List<String> strings, String fileName) {
         try {
             FileWriter writer = new FileWriter(fileName, true);
 
@@ -145,7 +145,7 @@ public class Main {
         }
     }
 
-    private static void uniques(String fileName) throws Exception {
+    public static void uniques(String fileName) throws Exception {
         List<String> lines = readLines(System.getProperty("user.dir") + "/" + fileName);
         HashSet<String> user = new HashSet<>();
         for (String l : lines) {

### 2015-12-16 project/src/NobelPrize.java

@@ -1,0 +1,42 @@
+import org.apache.jena.query.*;
+
+import java.io.IOException;
+import java.util.List;
+import java.util.stream.Collectors;
+
+/**
+ * Created by warreee on 12/16/15.
+ */
+public class NobelPrize {
+
+    public static void main(String[] args) throws Exception {
+        nobelQuery("allnobelwinners.rq");
+        Main.uniques("data.csv");
+    }
+
+    private static void nobelQuery(String queryFile) throws IOException {
+        String queryString = Main.readFile(System.getProperty("user.dir") + "/queries/" + queryFile);
+        Query query = QueryFactory.create(queryString);
+        QueryExecution qexec = QueryExecutionFactory.sparqlService("http://data.nobelprize.org/sparql", query);
+
+        try {
+            ResultSet results = qexec.execSelect();
+
+
+            for (; results.hasNext(); ) {
+                QuerySolution solution = results.nextSolution();
+                System.out.println(results.getResultVars());
+                for (String str: results.getResultVars()){
+                    System.out.println(Main.getSolutionLiteral(solution,str));
+                }
+                //List<String> res = results.getResultVars().stream().map(rv -> Main.getSolutionLiteral(solution, rv)).collect(Collectors.toList());
+                //Main.writeToCSV(res, "data.csv");
+                //System.out.println(solution);
+            }
+
+
+        } finally {
+            qexec.close();
+        }
+    }
+}

### 2015-12-16 project/src/Main.java
imgages

@@ -84,7 +84,8 @@ public class Main {
     }
 
 
-<<<<<<< HEAD
+
+    
     public static String readFile(String path)
             throws IOException {
         byte[] encoded = Files.readAllBytes(Paths.get(path));
@@ -124,12 +125,12 @@ public class Main {
         }
 
         System.out.println(user.size());
-=======
+
     private static String readFile(String path, Charset encoding)
             throws IOException {
         byte[] encoded = Files.readAllBytes(Paths.get(path));
         return new String(encoded, encoding);
->>>>>>> b019cd76a76e35735647ab50b7a1d931bd448cc3
+
     }
 
 }

### 2015-12-16 project/src/Main.java
main

@@ -1,12 +1,14 @@
 import org.apache.jena.query.*;
 import org.apache.jena.rdf.model.Model;
 import org.apache.jena.rdf.model.ModelFactory;
+import org.apache.jena.rdf.model.RDFNode;
 
 import java.io.*;
 import java.nio.charset.Charset;
 import java.nio.file.Files;
 import java.nio.file.Paths;
 import java.util.ArrayList;
+import java.util.HashSet;
 import java.util.List;
 import java.util.stream.Collector;
 import java.util.stream.Collectors;
@@ -15,24 +17,58 @@ public class Main {
 
     private List<String> strings = new ArrayList<>();
 
-    public static void main(String[] args) throws IOException {
-        outerQuery();
+    public static void main(String[] args) throws Exception {
+
+        //outerQuery();
+        dbPedia("scientist.rq");
+        dbPedia("politician.rq");
+        dbPedia("economist.rq");
+        dbPedia("writer.rq");
+        uniques("data.csv");
     }
 
-    private static void outerQuery() throws IOException {
-        String queryString = readFile(System.getProperty("user.dir") + "/queries/ToEpoliticians.rq", Charset.defaultCharset());
+    private static void dbPedia(String queryFile) throws IOException {
+        String queryString = readFile(System.getProperty("user.dir") + "/queries/" + queryFile);
         Query query = QueryFactory.create(queryString);
-        QueryExecution qexec = QueryExecutionFactory.sparqlService("http://linkedpolitics.ops.few.vu.nl/sparql/", query);
+        QueryExecution qexec = QueryExecutionFactory.sparqlService("http://dbpedia.org/sparql/", query);
 
         try {
             ResultSet results = qexec.execSelect();
 
+
+            for (; results.hasNext(); ) {
+                QuerySolution solution = results.nextSolution();
+                System.out.println(solution);
+                List<String> res = results.getResultVars().stream().map(rv -> getSolutionLiteral(solution, rv)).collect(Collectors.toList());
+                writeToCSV(res, "data.csv");
+                System.out.println(solution);
+            }
+
+
+        } finally {
+            qexec.close();
+        }
+    }
+
+    private static void outerQuery() throws IOException {
+        String queryString = readFile(System.getProperty("user.dir") + "/queries/ToEpoliticians.rq");
+        Query query = QueryFactory.create(queryString);
[…]

### 2015-12-16 project/src/NobelPrize.java
git

@@ -26,12 +26,10 @@ public class NobelPrize {
             for (; results.hasNext(); ) {
                 QuerySolution solution = results.nextSolution();
                 System.out.println(results.getResultVars());
-                for (String str: results.getResultVars()){
-                    System.out.println(Main.getSolutionLiteral(solution,str));
-                }
-                //List<String> res = results.getResultVars().stream().map(rv -> Main.getSolutionLiteral(solution, rv)).collect(Collectors.toList());
-                //Main.writeToCSV(res, "data.csv");
-                //System.out.println(solution);
+
+                List<String> res = results.getResultVars().stream().map(rv -> Main.getSolutionLiteral(solution, rv)).collect(Collectors.toList());
+                Main.writeToCSV(res, "data.csv");
+                System.out.println(solution);
             }
 
 

### 2015-12-16 project/src/NobelPrize.java
broken queries fixed

@@ -10,7 +10,7 @@ import java.util.stream.Collectors;
 public class NobelPrize {
 
     public static void main(String[] args) throws Exception {
-        nobelQuery("allnobelwinners.rq");
+        //nobelQuery("allnobelwinners.rq");
         Main.uniques("data.csv");
     }
 

### 2015-12-16 project/scripts/getScholarRanking.pl
scholar rankings

@@ -18,7 +18,7 @@ $url->query_form(
 # Initialize user agent
 $ua = LWP::UserAgent->new;
 $ua->timeout(10);
-$ua->agent("Mozilla/5.0");
+$ua->agent("Mozilla/5.0 (Macintosh; Intel Mac OS X 10_11_1) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/47.0.2526.80 Safari/537.36");
 
 # Get content and parse number of results
 $html = $ua->get($url);

### 2015-12-16 project/scripts/getScholarRankings.pl

@@ -1,0 +1,16 @@
+#!/usr/bin/perl
+
+open $file, '<', "../data/names.csv";
+open $out, '>', "../data/scholarrankings.csv";
+
+$i = 0;
+while (<$file>) {
+  chomp;
+  $n = `perl getScholarRanking.pl "$_"`;
+  print $out "$n\n";
+  print "$i\t$_\t$n\n";
+  $i++;
+}
+
+close $out;
+close $file;

### 2015-12-28 project/scripts/getScholarRankings.pl
wut

@@ -2,11 +2,20 @@
 
 open $file, '<', "../data/names.csv";
 open $out, '>', "../data/scholarrankings.csv";
+open $prox, '<', "proxies3.txt";
+
+@proxies;
+while (<$prox>) {
+  chomp;
+  push @proxies, $_;
+}
+
 
 $i = 0;
 while (<$file>) {
   chomp;
-  $n = `perl getScholarRanking.pl "$_"`;
+  $proxy = $proxies[rand @proxies];
+  $n = `perl getScholarRanking.pl \"$_\" http://$proxy`;
   print $out "$n\n";
   print "$i\t$_\t$n\n";
   $i++;

### 2015-12-28 project/scripts/getProxies.pl
New scraper.

@@ -1,0 +1,28 @@
+#!/usr/bin/perl
+# from https://phl4nk.wordpress.com/2015/04/11/perl-proxy-scraper/
+# fixed by KaW G7
+
+use strict;
+use warnings;
+use WWW::Mechanize;
+use Try::Tiny;
+
+my $source_file = shift . ".txt";
+
+open (INPUT_FILE, "<$source_file")  || die "Can't open $source_file: $!\n";
+
+my $crawler = WWW::Mechanize->new();
+
+while(<INPUT_FILE>) {
+  chomp;
+  try {
+    $crawler->get($_);
+    # hunt for IP:PORT combination
+    my @ips = $crawler->text() =~ /(\d{1,3}\.\d{1,3}\.\d{1,3}\.\d{1,3}\:\d{1,5})/g;
+    foreach (@ips){
+      print "$_\n";
+    }
+  } catch {
+    warn "[!] Error: $_ \n";
+  }
+}

### 2015-12-28 project/scripts/getScholarRanking.pl

@@ -1,6 +1,7 @@
   #!/usr/bin/perl
 
 use LWP::UserAgent;
+use HTTP::Cookies::Netscape;
 use URI;
 
 ($name, $proxy) = @ARGV;
@@ -14,21 +15,37 @@ if (not defined $name) {
 $url = URI->new('http://scholar.google.be/scholar');
 $url->query_form(
   "hl" => "nl",
-  "q"  => "author:$name"
+  "q"  => "author:\"$name\""
 );
 
-# Initialize user agent
+# Initialize cookie jar
+$cookiejar = HTTP::Cookies::Netscape->new(
+  file => 'cookies.dat',
+  # autosave => 1
+);
+
+# Initialize user agent and co
 $ua = LWP::UserAgent->new;
 $ua->timeout(10);
+$ua->cookie_jar($cookiejar);
 if (defined $proxy) {
   $ua->proxy('http', $proxy);
 }
-$ua->agent("Mozilla/5.0 (Macintosh; Intel Mac OS X 10_11_1) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/47.0.2526.80 Safari/537.36");
-
+$ua->agent("Mozilla/5.0");
 
 # Get content and parse number of results
 $html = $ua->get($url);
-print $html->content();
-$html->content() =~ /Ongeveer\s(.+?)\sresultaten/;
 
-# print $1;
+if ($html->content() =~ /geen artikelen/) {
+  print "0";
+} elsif ($html->content() =~ /1 resultaat/) {
+  print "1";
+} else {
+  $html->content() =~ /(\d+\.?\d*\.?\d*)\sresultaten/;
+  if (not defined $1) {
+    print "";
+  #   # print $html->content();
+  } else {
+    print $1;
+  }
+}

### 2015-12-28 project/scripts/getScholarRankings.pl

@@ -1,25 +1,132 @@
 #!/usr/bin/perl
 
-open $file, '<', "../data/names.csv";
-open $out, '>', "../data/scholarrankings.csv";
-open $prox, '<', "proxies3.txt";
+use LWP::UserAgent::ProxyHopper;
+use Data::Dumper;
+use List::Util qw(shuffle);
 
-@proxies;
-while (<$prox>) {
-  chomp;
-  push @proxies, $_;
+$MAX = 10;
+$PROXY = 0;
+$TIMING = 1;
+
+sub checkIfLive {
+  ($p) = @_;
+  $ua = LWP::UserAgent->new;
+  $ua->timeout(10);
+  $ua->proxy('http', "$p");
+  $ua->agent("Mozilla/5.0");
+  $h = $ua->get('http://scholar.google.be/scholar?q=author%3A%22Andrew+Gwynne%22');
+  if ($h->content() =~ /1 resultaat/) {
+    # print $h->content();
+    return 1;
+  } else {
+    return 0;
+  }
 }
 
+open $file, '<', "../data/scholarrankings.csv";
+open $prox, '<', "proxies.txt";
 
-$i = 0;
+print ".-------------------------------------.\n";
+print "| G7's Google Scholar Rank Downloader |\n";
+print "'-------------------------------------'\n";
+
+# Read all names
+%rankings = {};
+$toFind = 0;
 while (<$file>) {
   chomp;
-  $proxy = $proxies[rand @proxies];
-  $n = `perl getScholarRanking.pl \"$_\" http://$proxy`;
-  print $out "$n\n";
-  print "$i\t$_\t$n\n";
-  $i++;
+  @s = split ',', $_;
+  if ($#s == 0) {
+    $rankings{$s[0]} = "";
+    $toFind++;
+  } else {
+    $rankings{$s[0]} = $s[1];
+  }
 }
 
-close $out;
+print " -> Still need to scrape $toFind results.\n";
+
+if ($MAX < $toFind) {
+  print " -> Finding next $MAX.\n";
+  $toFind = $MAX;
+}
+$neededProxies = int($toFind / 10);
+
+if ($PROXY == 1) {
+  print " -> Searching live proxies, we need about $neededProxies.\n";
+
+  @iproxies;
+  while (<$prox>) {
+    chomp;
+    push @iproxies, "http://$_";
+  }
+  $pua = LWP::UserAgent::ProxyHopper->new(
[…]

### 2015-12-28 project/src/Main.java
new names file

@@ -21,7 +21,8 @@ public class Main {
     public static void main(String[] args) throws Exception {
 
         //outerQuery();
-
+        dbPedia("scientist.rq");
+        dbPedia("economist.rq");
         uniques("data.csv");
     }
 

### 2015-12-29 project/src/Main.java
changed to semicoln

@@ -128,10 +128,10 @@ public class Main {
         try {
             FileWriter writer = new FileWriter(fileName, true);
 
+            writer.append(strings.get(0).replace("\n","") + " " + strings.get(1).replace("\n","")).append("; ");
+            for (int i = 2; i < strings.size() - 1; i++) {
 
-            for (int i = 0; i < strings.size() - 1; i++) {
-
-                writer.append(strings.get(i).replace("\n","")).append(", ");
+                writer.append(strings.get(i).replace("\n","")).append("; ");
             }
 
                 writer.append(strings.get(strings.size() - 1)).append("\n");
@@ -149,11 +149,11 @@ public class Main {
         HashSet<String> user = new HashSet<>();
         HashSet<String> names = new HashSet<>();
         for (String l : lines) {
-            String[] line = l.split(", ");
+            String[] line = l.split("; ");
 
-            user.add(line[0] + line[1]);
+            user.add(line[0]);
 
-            names.add(line[0] + " " + line[1] + "\n");
+            names.add(line[0] + "\n");
 
 
         }

### 2015-12-29 project/src/Main.java
no spaces

@@ -128,10 +128,10 @@ public class Main {
         try {
             FileWriter writer = new FileWriter(fileName, true);
 
-            writer.append(strings.get(0).replace("\n","") + " " + strings.get(1).replace("\n","")).append("; ");
+            writer.append(strings.get(0).replace("\n","") + " " + strings.get(1).replace("\n","")).append(";");
             for (int i = 2; i < strings.size() - 1; i++) {
 
-                writer.append(strings.get(i).replace("\n","")).append("; ");
+                writer.append(strings.get(i).replace("\n","")).append(";");
             }
 
                 writer.append(strings.get(strings.size() - 1)).append("\n");
@@ -149,7 +149,7 @@ public class Main {
         HashSet<String> user = new HashSet<>();
         HashSet<String> names = new HashSet<>();
         for (String l : lines) {
-            String[] line = l.split("; ");
+            String[] line = l.split(";");
 
             user.add(line[0]);
 

### 2015-12-29 project/src/Main.java
nobelwinners added

@@ -100,6 +100,9 @@ public class Main {
 
     public static String getSolutionLiteral(QuerySolution solution, String rv) {
         try {
+            if (rv.equals("by")){
+                return solution.getLiteral(rv).getValue().toString().substring(0,4);
+            }
             return solution.getLiteral(rv).getValue().toString();
         } catch (NullPointerException e) {
             return " ";
@@ -128,7 +131,7 @@ public class Main {
         try {
             FileWriter writer = new FileWriter(fileName, true);
 
-            writer.append(strings.get(0).replace("\n","") + " " + strings.get(1).replace("\n","")).append(";");
+            writer.append(strings.get(0).replace("\n", "") + " " + strings.get(1).replace("\n","")).append(";");
             for (int i = 2; i < strings.size() - 1; i++) {
 
                 writer.append(strings.get(i).replace("\n","")).append(";");

### 2015-12-30 project/scripts/getLikes.pl
new scripts!

@@ -1,0 +1,36 @@
+#!/usr/bin/perl
+
+use LWP::Simple;
+use URI;
+use JSON;
+use Data::Dumper;
+
+sub getLikes {
+  ($id) = @_;
+  $l_url = URI->new("https://graph.facebook.com/$id");
+  $l_url->query_form(
+    "access_token" => "CAACEdEose0cBAF7NlLzlnEMbGhw4bs4ejY1nSDRARxslWvpiuj62bNZCOpa55orMDOdAvVXGsGGO5A1kTuAzC8Rcgf4iiaCLagcCpLlgrShJQRvvASPhV8O8TnP01VLVjNIFQPfLpes8NWYQOCZB93XhZBHdPyrxLvIZBeMZAI9BbCrvOIln3YZAYiSopYzcXNTpfwZB3yXZBgZDZD",,
+    "fields" => "likes"
+  );
+  $res = decode_json get($l_url);
+  return $res->{'likes'};
+}
+
+# Build URI
+$url = URI->new('https://graph.facebook.com/search');
+$url->query_form(
+  "access_token" => "CAACEdEose0cBAF7NlLzlnEMbGhw4bs4ejY1nSDRARxslWvpiuj62bNZCOpa55orMDOdAvVXGsGGO5A1kTuAzC8Rcgf4iiaCLagcCpLlgrShJQRvvASPhV8O8TnP01VLVjNIFQPfLpes8NWYQOCZB93XhZBHdPyrxLvIZBeMZAI9BbCrvOIln3YZAYiSopYzcXNTpfwZB3yXZBgZDZD",
+  "q"  => "Bart de Wever",
+  "type" => "page"
+);
+
+# Get search results
+$html = get($url);
+$json = decode_json $html;
+@data = @{$json->{'data'}};
+
+foreach $page (@data) {
+  print "$page->{'name'}";
+  print getLikes $page->{'id'};
+  print "\n";
+}

### 2015-12-30 project/scripts/getUniversityRanking.pl

@@ -18,6 +18,7 @@ open $f, '<', $rankingFile;
 # Parse university scores
 %universityScores;
 while(<$f>) {
+	chomp;
   @u = split /;/, $_;
   $universityScores{$u[0]} = $u[1];
 }
@@ -30,6 +31,6 @@ foreach $u (keys %universityScores) {
   $universityDistances{$u} = pdistance($university, $u, $set, \&distance);
 }
 
-foreach $name (sort { $universityDistances{$a} <=> $universityDistances{$b} } keys %universityDistances) {
-    printf "%-8s %s\n", $name, $universityDistances{$name};
-}
+@sorted = sort { $universityDistances{$a} <=> $universityDistances{$b} }
+				  keys %universityDistances;
+print "$sorted[0] ($universityDistances{$sorted[0]})";

### 2015-12-30 project/scripts/mergeData.pl

@@ -1,0 +1,62 @@
+#!/usr/bin/perl
+
+use Data::Dumper;
+
+# Read DBPedia file.
+open $dbp, '<', '../data/DBPedia.csv';
+%data;
+while(<$dbp>) {
+  chomp;
+  ($name, $year, $country, $university) = split ";", $_;
+  if (defined $data{$name}) {
+    # Already exists, add university.
+    push $data{$name}{'university'}, $university;
+  } else {
+    # Create new entry.
+    $data{$name} = {
+      year => $year,
+      country => $country,
+      university => [$university]
+    };
+  }
+}
+
+# Read university scores
+$rankingFile = "../data/rankings.csv";
+if (not -e $rankingFile) {
+  `perl getRankings.pl rankings`;
+}
+open $f, '<', $rankingFile;
+%universityScores;
+while(<$f>) {
+  chomp;
+  @u = split /;/, $_;
+  $universityScores{$u[0]} = $u[1];
+}
+
+@notFound = ();
+$found = 0;
+foreach $k (keys %data) {
+  $universities = $data{$k}{'university'};
+  foreach $u (@$universities) {
+    if (not defined $universityScores{$u}) {
+      if (not grep /^$u$/, @notFound) {
+        push @notFound, $u;
+      }
+    } else {
+      $found++;
+      last;
+    }
+  }
+}
+
+print " -> Found $found scientists with ranked university.\n";
+print " -> Didn't find " . ($#notFound + 1) . " universities.\n";
+print " -> Performing fuzzy search.\n";
+# 
+# foreach $u (@notFound) {
+#   $match = `perl getUniversityRanking.pl \"$u\"`;
+#   print "\t$u -> $match\n";
+# }
+# print "$notFound[0]\n";
+# print `perl getUniversityRanking.pl $notFound[0]`;

### 2015-12-30 project/src/Main.java
new names.csv

@@ -21,8 +21,8 @@ public class Main {
     public static void main(String[] args) throws Exception {
 
         //outerQuery();
-        dbPedia("scientist.rq");
-        dbPedia("economist.rq");
+        //dbPedia("scientist.rq");
+        //dbPedia("economist.rq");
         uniques("data.csv");
     }
 

### 2015-12-30 project/src/Main.java
merged file

@@ -1,17 +1,13 @@
 import org.apache.jena.query.*;
-import org.apache.jena.rdf.model.Model;
-import org.apache.jena.rdf.model.ModelFactory;
-import org.apache.jena.rdf.model.RDFNode;
-import org.apache.jena.tdb.store.Hash;
 
-import java.io.*;
+import java.io.FileWriter;
+import java.io.IOException;
 import java.nio.charset.Charset;
 import java.nio.file.Files;
 import java.nio.file.Paths;
 import java.util.ArrayList;
 import java.util.HashSet;
 import java.util.List;
-import java.util.stream.Collector;
 import java.util.stream.Collectors;
 
 public class Main {
@@ -21,9 +17,11 @@ public class Main {
     public static void main(String[] args) throws Exception {
 
         //outerQuery();
-        //dbPedia("scientist.rq");
-        //dbPedia("economist.rq");
-        uniques("data.csv");
+        dbPedia("scientist.rq");
+        dbPedia("economist.rq");
+        NobelPrize.nobelQuery("allnobelwinners.rq");
+        removeAmbiguity("data.csv");
+        uniques("yesno.csv");
     }
 
     private static void dbPedia(String queryFile) throws IOException {
@@ -39,7 +37,7 @@ public class Main {
                 QuerySolution solution = results.nextSolution();
                 System.out.println(solution);
                 List<String> res = results.getResultVars().stream().map(rv -> getSolutionLiteral(solution, rv)).collect(Collectors.toList());
-                writeToCSV(res, "data.csv");
+                writeToCSV(res, false, "data.csv");
                 System.out.println(solution);
             }
 
@@ -87,7 +85,7 @@ public class Main {
             for (; results.hasNext(); ) {
                 QuerySolution solution = results.nextSolution();
                 List<String> res = results.getResultVars().stream().map(rv -> getSolutionLiteral(solution, rv)).collect(Collectors.toList());
-                writeToCSV(res, "data.csv");
+                writeToCSV(res, false, "data.csv");
                 System.out.println(solution);
             }
 
@@ -100,8 +98,8 @@ public class Main {
 
     public static String getSolutionLiteral(QuerySolution solution, String rv) {
         try {
-            if (rv.equals("by")){
-                return solution.getLiteral(rv).getValue().toString().substring(0,4);
+            if (rv.equals("by")) {
+                return solution.getLiteral(rv).getValue().toString().substring(0, 4);
             }
             return solution.getLiteral(rv).getValue().toString();
         } catch (NullPointerException e) {
[…]

### 2015-12-30 project/src/NobelPrize.java

@@ -14,7 +14,7 @@ public class NobelPrize {
         Main.uniques("data.csv");
     }
 
-    private static void nobelQuery(String queryFile) throws IOException {
+    public static void nobelQuery(String queryFile) throws IOException {
         String queryString = Main.readFile(System.getProperty("user.dir") + "/queries/" + queryFile);
         Query query = QueryFactory.create(queryString);
         QueryExecution qexec = QueryExecutionFactory.sparqlService("http://data.nobelprize.org/sparql", query);
@@ -28,7 +28,7 @@ public class NobelPrize {
                 System.out.println(results.getResultVars());
 
                 List<String> res = results.getResultVars().stream().map(rv -> Main.getSolutionLiteral(solution, rv)).collect(Collectors.toList());
-                Main.writeToCSV(res, "data.csv");
+                Main.writeToCSV(res, true, "data.csv");
                 System.out.println(solution);
             }
 
@@ -37,4 +37,5 @@ public class NobelPrize {
             qexec.close();
         }
     }
+
 }

### 2015-12-30 project/scripts/mergeData_lessWords.pl
Create mergeData_lessWords.pl

@@ -1,0 +1,63 @@
+#!/usr/bin/perl
+
+use Data::Dumper;
+
+# Read DBPedia file.
+open $dbp, '<', '../data/mergedDBpediaNobel2_lessWords.csv';
+%data;
+while(<$dbp>) {
+  chomp;
+  ($name, $year, $country, $university) = split ";", $_;
+  if (defined $data{$name}) {
+    # Already exists, add university.
+    push $data{$name}{'university'}, $university;
+  } else {
+    # Create new entry.
+    $data{$name} = {
+      year => $year,
+      country => $country,
+      university => [$university]
+    };
+  }
+}
+
+# Read university scores
+$rankingFile = "../data/rankings2_lessWords.csv";
+if (not -e $rankingFile) {
+  `perl getRankings.pl rankings`;
+}
+open $f, '<', $rankingFile;
+%universityScores;
+while(<$f>) {
+  chomp;
+  @u = split /;/, $_;
+  $universityScores{$u[0]} = $u[1];
+}
+
+# Match universities
+@notFound = ();
+$found = 0;
+foreach $k (keys %data) {
+  $universities = $data{$k}{'university'};
+  foreach $u (@$universities) {
+    if (not defined $universityScores{$u}) {
+      if (not grep /^$u$/, @notFound) {
+        push @notFound, $u;
+      }
+    } else {
+      $found++;
+      last;
+    }
+  }
+}
+
+print " -> Found $found scientists with ranked university.\n";
+print " -> Didn't find " . ($#notFound + 1) . " universities.\n";
+print " -> Performing fuzzy search.\n";
+
+#foreach $u (@notFound) {
+#   $match = `perl getUniversityRanking.pl \"$u\"`;
+#   print "\t$u -> $match\n";
+# }
+#print "$notFound[0]\n";
+#print `perl getUniversityRanking.pl $notFound[0]`;

### 2016-01-10 project/src/Main.java
added new label

@@ -6,6 +6,7 @@ import java.nio.charset.Charset;
 import java.nio.file.Files;
 import java.nio.file.Paths;
 import java.util.ArrayList;
+import java.util.Arrays;
 import java.util.HashSet;
 import java.util.List;
 import java.util.stream.Collectors;
@@ -17,10 +18,10 @@ public class Main {
     public static void main(String[] args) throws Exception {
 
         //outerQuery();
-        dbPedia("scientist.rq");
-        dbPedia("economist.rq");
-        NobelPrize.nobelQuery("allnobelwinners.rq");
-        removeAmbiguity("data.csv");
+        //dbPedia("scientist.rq");
+        //dbPedia("economist.rq");
+        //NobelPrize.nobelQuery("allnobelwinners.rq");
+        //removeAmbiguity("data.csv");
         uniques("yesno.csv");
     }
 
@@ -135,9 +136,9 @@ public class Main {
                 writer.append(strings.get(i).replace("\n", "").replace(";"," ")).append(";");
             }
             if (nobel) {
-                writer.append("yes\n");
+                writer.append("nobel;yes\n");
             } else {
-                writer.append("no\n");
+                writer.append("economist;no\n");
             }
 
 
@@ -178,6 +179,9 @@ public class Main {
                     String[] line2 = l2.split(";");
                     if (laur.equals(line2[0]) && line2[line2.length-1].equals("no")) {
                         newLines.remove(l2);
+                        newLines.remove(l);
+                        line[line.length-2] = line2[line2.length-2];
+                        newLines.add(String.join(";",line));
                     }
                 }
             }

### 2016-01-10 project/src/NobelPrize2.java

@@ -7,7 +7,7 @@ import java.util.stream.Collectors;
 /**
  * Created by warreee on 12/16/15.
  */
-public class NobelPrize {
+public class NobelPrize2 {
 
     public static void main(String[] args) throws Exception {
         //nobelQuery("allNobelNames.rq", "allNobelNames.csv");
@@ -41,7 +41,7 @@ public class NobelPrize {
     
     // Get all universities of nobel prize winners from nobelprize.org which were not found on dbpedia
     public static void nobelQuery2(String namesFile, String queryFile, String resultFile, String notFoundFile) throws IOException {
-    	Main.getUniversitiesOfPersons("allNobelNames_notOnDBPedia.csv", "almaMaterOfPerson_nobel.rq", "almaMaterOfPersonNobel.csv", "allNobelNames_notOnNobel.csv", "http://data.nobelprize.org/sparql");
+    	Main2.getUniversitiesOfPersons("allNobelNames_notOnDBPedia.csv", "almaMaterOfPerson_nobel.rq", "almaMaterOfPersonNobel.csv", "allNobelNames_notOnNobel.csv", "http://data.nobelprize.org/sparql");
     }
 
 }

### 2016-01-12 project/scripts/mergeData.pl
More google.

@@ -2,9 +2,20 @@
 
 use Data::Dumper;
 
+$dFile = "mergedDBpediaNobelNewUni_Final.csv";
+$uFile = "rankings_final.csv";
+$lFile = "likes.csv";
+$sFile = "scholarrankings.csv";
+
+%data;              # Main data file
+%rankings;  # University rankings
+%likes;             # Likes
+%scholar;           # Scholar rankings
+
+# READ EVERYTHING
+
 # Read DBPedia file.
-open $dbp, '<', '../data/DBPedia.csv';
-%data;
+open $dbp, '<', "../data/$dFile";
 while(<$dbp>) {
   chomp;
   ($name, $year, $country, $university) = split ";", $_;
@@ -22,38 +33,59 @@ while(<$dbp>) {
 }
 
 # Read university scores
-$rankingFile = "../data/rankings.csv";
-if (not -e $rankingFile) {
-  `perl getRankings.pl rankings`;
-}
-open $f, '<', $rankingFile;
-%universityScores;
-while(<$f>) {
+open $rf, '<', "../data/$uFile";
+while(<$rf>) {
   chomp;
   @u = split /;/, $_;
-  $universityScores{$u[0]} = $u[1];
+  $rankings{$u[0]} = $u[1];
 }
 
-# Match universities
-@notFound = ();
-$found = 0;
-foreach $k (keys %data) {
-  $universities = $data{$k}{'university'};
-  foreach $u (@$universities) {
-    if (not defined $universityScores{$u}) {
-      if (not grep /^$u$/, @notFound) {
-        push @notFound, $u;
-      }
-    } else {
-      $found++;
-      last;
-    }
-  }
+# Read likes
+open $lf, '<', "../data/$lFile";
+while(<$lf>) {
+  chomp;
+  @l = split /;/, $_;
+  $likes{$l[0]} = $l[1];
 }
 
-print " -> Found $found scientists with ranked university.\n";
-print " -> Didn't find " . ($#notFound + 1) . " universities.\n";
-print " -> Performing fuzzy search.\n";
+# Read scholar rankings
+open $sf, '<', "../data/$sFile";
+while(<$sf>) {
+  chomp;
+  @s = split /,/, $_;
+  $scholar{$s[0]} = $s[1];
+}
+
+# MERGE EVERYTHING
+
+foreach $name (keys %data) {
+  $data{$name}{'likes'} = $likes{$name};
+  $data{$name}{'scholar'} = $scholar{$name};
+  print Dumper($data{$name});
+  last;
[…]

### 2016-01-16 project/paper/appendices/productivity.tex
Paper: alles t.e.m. data is klaar. Discussie work productity begin al geschreven.

\section{Discussion on work productivity}

Whether we can use different proxy measures for a certain feature is a sensitive issue. For this reason, we here provide a more thorough discussion of the matter. First, we discuss why we have to use different categories of people for building the model and training it. This introduces the problem of having to proxy a feature using  different measures. Next, we discuss why we believe the chosen measures might be a good proxy for the productivity feature. Finally, we give a weakened version of the research question that is now more appropriately answered.

\subsection{Different datasets}

The assignment was to find a research question revolving around the knowledge base, enriched with information from other sources. Because we found an interesting knowledge base on Nobel Prizes, the posed research question wasn't a far fetch. The problem is that in order to build a model on who would win a Nobel Prize, we need positive and negative examples. The positive examples are the Nobel laureates, which come from a pool of scientists. All other scientists naturally serve as negative examples. Since a politician isn't eligible to receive such prize, we can't use them as negative examples. It is thus inevitable to use different examples in the training set and the testing set.

\subsection{Work productivity}

Apart from university rankings and popularity measures, work productivity seems like a reasonable feature to use in order to assess eligibility to receive an award. We reason that hard work will more likely result in making some scientific breakthrough, which increases the chances of someone winning a Nobel Prize. The productivity feature is not trivial to define, however. Furthermore, even if we can define it, all information needed to compute it has to be available for as many training and testing instances as possible. We therefore view all examples as \emph{persons} rather than \emph{scientists} or \emph{politicians}, having certain properties. How we define the work productivity property is the only difference between both datasets. For scientists, the number of publications seems like a decent way of measuring how productive they've been. For politicians, the most resemblant feature would have been the number of legislations they managed to get accepted. This information isn't publicly available, however, so we looked at something else. Coming straight from the ToE knowledge base, the number of speeches at european parliament seemed a good proxy measure. Both are numeric properties which we can normalise to $[0, 100]$.

\subsubsection{Work productivity duality}
An interesting duality exists in both measures. Having a lot of publications over a mediocre amount can be recognised by the model as either a \emph{good} or \emph{bad} property. It can for example mean that someone is just trying to publish a lot of less significant results, while a mediocre amount of significant results might be more important. For speeches the same happens, where a lot of speeches might just as well mean that a politician is only talking, without actually \emph{doing} much. This re\"inforces our belief that both might be a good proxy for the same feature.

\subsection{Weakened research question}
A more appropriate version of the research question is then
\begin{center}
	\emph{\textbf{\textsc{IF}} the number of publications and the number of speeches in European Parliament are reliable proxies for the work productivity of scientists and politicians respectively \textbf{\textsc{THEN}} which European politicians have a high chance of receiving a Nobel Prize?}
\end{center}

### 2016-01-16 project/paper/sections/analysis.tex
Paper: alles t.e.m. data is klaar. Discussie work productity begin al geschreven.

\section{Data analysis}
\label{sec:analysis}

\subsection{Quality assessment}
\label{ssec:quality}
\todo[inline]{Alinea over hoe we data samen zetten. Name matching, problemen hierbij, Aantal entries in training dataset en research set, aantal positieve voorbeelden t.o.v. negatieve voorbeelden (en vermelden dat dit een probleem is en hoe we dit oplossen/compenseren), andere statistieken i.v.m. data, outliers}

\subsection{Learning a model}

\todo[inline]{Statistieken i.v.m training en research sets hier?}

\todo[inline]{figuren hier ter visualisatie data}

\todo[inline]{Sectie over difficulties (training data veel negatieve en weinig positieve examples, links die er niet zijn}

### 2016-01-16 project/paper/sections/data.tex
Paper: alles t.e.m. data is klaar. Discussie work productity begin al geschreven.

\section{Data}
\label{sec:data}

First, we determine features of people that might influence their probability of winning a Nobel Prize. They are elaborated in Section~\ref{ssec:features}. Next, we research whether and where this information can be found. The main data source are knowledge bases, also known as Linked Open Data in the Semantic Web. We can use SPARQL queries on an endpoint to easily retrieve structured data \cite{wc3SPARQL}. The used knowledge bases discussed in Section~\ref{ssec:knowledgebases}. Needed information that is not (yet) linked has to be scraped from websites. These are discussed in Section~\ref{ssec:additional}. We use Perl scripts and regular expressions to extract the data from plain HTML text. And outline of this is given in Appendix ?B?.

\subsection{Feature selection}
\label{ssec:features}
In order to determine whether someone will win a Nobel Prize, a set of reasonable features that the model can base its decisions on is needed. A summary of the chosen features is given here. 
\begin{itemize}
\item \textbf{Year and data of birth.}
Currently the average age of a laureate is 59 \cite{age}. Evidently, this plays a role in the decision if somebody makes a chance for a Nobel Prize. For example, young scientists are far less likely to win an award because they have yet to prove themselves.
\item \textbf{Alma mater.} We suppose that there's a link between the university where one graduated and his chances of winning a Nobel Prize. For example, admission to prestige universities is only granted to the best candidates. In order to extract a usable feature from an alma mater, we use its \emph{award score}, which is based on how many Nobel Prize and Field medal winners it produced. In case someone has studied are multiple universities that have a score higher than 0, the average is used. Unranked universities automatically have a score of 0 (which is an inherent property of how it is calculated).
\item \textbf{Work productivity.} A measure of work productivity can also be useful to include. This is however not trivial to determine as not many properties are available for the majority of scientists and politicians. In order to solve this, we attempted defining a \textbf{proxy} measure for work productivity for the training data and testing individuals. For the scientists and economists from the training dataset, their number of publications might be an appropriate measure for productivity. For politicians, the number of speeches they make are perhaps a good indication of how productive they are. \emph{Because this is a sensitive subject, Appendix ?A? provides a thorough discussion of why we chose these features and how the research question is slightly weakened by our assumption. Furthermore, in Section~\ref{ssec:quality} on quality assessment, we show why we deem both to be a reasonable proxy by comparing their distributions.}
\item \textbf{Popularity.} A popularity measure is easier to define. Facebook automatically generates pages for individuals that exist on Wikipedia. Therefore all people that we consider have at least such automatically generated page. The number of likes these pages have can then serve as a measure for popularity. 
\end{itemize}

\subsection{Knowledge bases}
\label{ssec:knowledgebases}

Using SPARQL queries, knowledge bases are very easy to retrieve structured information from. Three knowledge bases that we used are listed and discussed below.

\begin{itemize}
\item{\textbf{DBpedia}} is a Linked Open Data source which contains information for just about everything. Coming straight from Wikipedia, it is updated daily and should thus be up-to-date all the time. Although it can be edited by anyone, data correctness is verified thoroughly by a team of content moderators. For this reason we get a large part of our training set data from DBpedia. More specifically, we retrieve the year and country of birth, as well as alma mater and of course their full name. The name mostly serves as an identifier for linking data from multiple sources. Persons for which not all data is found are immediately omitted.

\item{\textbf{Nobelprize.org}} is the most complete Linked Open Data source concerning Nobel Prize winners. From 1901 on, it contains all Nobel Prizes that have been won. Moreover, it is maintained by the official organisation responsible for the Nobel Prize and should thus be complete and correct. Since it makes use of the FOAF and DBpedia ontologies, querying it is very easy. The most important feature that we retrieve from this source is of course whether someone has won a Nobel Prize. One thing missing is a \emph{sameAs:} link to DBPedia, which makes our task of linking it slightly harder.

\item{\textbf{Talk of Europe}} is a Linked Open Data source about the European Parliament. The dataset covers all plenary debates held in the European Parliament between July 1999 and January 2014 and biographical information about the members of parliament. The politicians in this data source are the ones for which we would like to answer the research question. Using a \emph{sameAs:} relation to DBPedia, we can easily query for further information without needing exact name matches.
\end{itemize}

\noindent All SPARQL queries used to gather the needed information are shown in Appendix ??.

\subsection{Additional data}
\label{ssec:additional}

For the work productivity, university rankings and popularity features no linked data exists. We therefore scraped all needed information from webpages and linked them ourselves. This was done using Perl scripts and regular expressions, with varying difficulty for different sources.

\begin{itemize}
\item{\textbf{Shanghai Rankings. }} 	
The page at \cite{rankings} gives an overview of the Shanghai Rankings for 2015. It also includes  information on the criteria used to build this ranking, which includes the awards ranking. Universities that are not listed have an award ranking of 0. Because of tabular form, retrieving the data was fairly straightforward.

\item{\textbf{Facebook. }} As mentioned, every person on Wikipedia has an automatically generated Facebook page. Querying Facebook can be done using the Graph API with simple HTTP GET requests \cite{graphAPI}. Specialised queries can be constructed using combinations of GET parameters, for which the results are returned in JSON format. Because of this, out of all non-linked sources, information from Facebook was by far the easiest to gather. For people with multiple pages, the number of liked for the most liked page is used. Because popular names might have pages not related to the scientist we are interested in, some results might be noisy. Such outliers have to be pruned afterwards.

\item{\textbf{Google Scholar. }} Google Scholar provides advanced search options, the most relevant for us is searching by author. In contrary to Facebook this not achieved by combining GET parameters, but by manually constructing the advanced search terms. For example, to search for publications by Albert Einstein the query  \emph{author:"Albert Einstein"} can be used. The resulting page shows the number of results, which we can then parse. Based on manual testing, Google's advanced search performs pretty well for finding only results for a given author. However, as before, people with the same name can give noisy results, so some outlier detection has to be performed. A second difficulty arose when Google appeared to block automated requests. Appendix ?? gives an overview of some methods we used in attempt to moderately successfully circumvent those restrictions.
\end{itemize}

\subsection{Overview}

The following table gives an overview of which feature information was collected from what sources. Linked Open Data sources are shown in \textbf{bold}.

\begin{table}[H]
\centering
\begin{tabular}{l|l}
	\textbf{\textsc{Feature}} & \textbf{\textsc{Source}} \\ \hline
	\rule{0pt}{4mm}Place of birth & \textbf{DBPedia} \\
	Year of birth & \textbf{DBPedia} \\
	University ranking & \textbf{DBPedia} + Shanghai Ranking 2015\\
	Work Productivity & Google Scholar, \textbf{ToE}\\
	Popularity & Facebook\\
	Nobel Prize& \textbf{Nobelprize.org}
\end{tabular}
\caption{Overview of used features and their respective sources.}
\end{table}

\subsection{Processing and merging}

After collecting the data from different sources, it has to be combined in some way. For the most part, this was pretty easy by matching names. The hardest part was matching universities from DBPedia to those retrieved by scraping the ARWU rankings.

### 2016-01-16 project/paper/sections/methodology.tex
Paper: alles t.e.m. data is klaar. Discussie work productity begin al geschreven.

\section{Methodology}
\label{sec:methodology}
To answer the research question we will use the approach described below. The next sections will explain the steps more thoroughly.
\begin{enumerate}
\item We think about what properties of previous Nobel Prize winners might be interesting to incorporate in learning a model. This is the feature selection step. Furthermore, we determine whether and where this information can be found.
\item The available data is then collected by the aid of SPARQL queries and scraping webpages. This is combined into a training dataset and a research dataset. The training dataset consist of all features for scientists and economists that have or have not won a Nobel Prize. This can be used to learn a predictive model. The research data set contains the same features, but then for politicians for which we would like to answer the research question.
\item Some statistics are applied to the training data to assess its quality. For example, because collecting the data is prone to errors, some outlier detection and removal has to be perfomed.
\item The final training dataset is used to learn a model that is able to predict how likely a person is to win a Nobel Prize. A logistic regression model is used. Because it predicts the probability of particular outcomes, it is perfectly suited to answer the research question. The model's accuracy is assessed using cross-validation on the training dataset.
\item The final step is applying the learned model on the training dataset and discussing its results. 
\end{enumerate}

### 2016-01-16 project/scripts/mergeData.pl

@@ -2,13 +2,13 @@
 
 use Data::Dumper;
 
-$dFile = "mergedDBpediaNobelNewUni_Final.csv";
+$dFile = "mergedDBpediaNobelNewUni_economist_or_scientist_Final.csv";
 $uFile = "rankings_final.csv";
 $lFile = "likes.csv";
 $sFile = "scholarrankings.csv";
 
 %data;              # Main data file
-%rankings;  # University rankings
+%rankings;          # University rankings
 %likes;             # Likes
 %scholar;           # Scholar rankings
 
@@ -18,7 +18,7 @@ $sFile = "scholarrankings.csv";
 open $dbp, '<', "../data/$dFile";
 while(<$dbp>) {
   chomp;
-  ($name, $year, $country, $university) = split ";", $_;
+  ($name, $year, $country, $university, $type) = split ";", $_;
   if (defined $data{$name}) {
     # Already exists, add university.
     push $data{$name}{'university'}, $university;
@@ -27,7 +27,8 @@ while(<$dbp>) {
     $data{$name} = {
       year => $year,
       country => $country,
-      university => [$university]
+      university => [$university],
+      type => $type
     };
   }
 }

### 2016-01-18 project/paper/sections/data.tex
some modifications to the paper

@@
 We can use SPARQL queries on an endpoint to easily retrieve structured data \cite{wc3SPARQL}.
-The used knowledge bases discussed in Section~\ref{ssec:knowledgebases}.
+The used knowledge bases are discussed in Section~\ref{ssec:knowledgebases}.
 Needed information that is not (yet) linked has to be scraped from websites.
@@
 We use Perl scripts and regular expressions to extract the data from plain HTML text.
-And outline of this is given in Appendix ?B?.
+All the retrieved data and all the used scripts can be found at the webpage for this paper: \url{kaw.wardschodts.ws}.
 
@@
 In order to extract a usable feature from an alma mater, we use its \emph{award score}, which is based on how many Nobel Prize and Field medal winners it produced.
-In case someone has studied are multiple universities that have a score higher than 0, the average is used.
-Unranked universities automatically have a score of 0 (which is an inherent property of how it is calculated).
+In case someone has studied at multiple universities that have a score higher than 0, the average is used.
+Unranked universities automatically have a score of 0 (which is an inherent property of how it is calculated) \todo[inline]{uitleggen wat er gebeurt als er een paar 0 zij}.
 \item \textbf{Work productivity.} A measure of work productivity can also be useful to include.
-This is however not trivial to determine as not many properties are available for the majority of scientists and politicians.
+This is however not trivial to determine, as not many properties are available for the majority of scientists and politicians.
 In order to solve this, we attempted defining a \textbf{proxy} measure for work productivity for the training data and testing individuals.
@@
 One thing missing is a \emph{sameAs:} link to DBPedia, which makes our task of linking it slightly harder.
+Our approach for merging this data with the other features is discussed in subsection \ref{ssec:merging}.
 
@@
 
-\noindent All SPARQL queries used to gather the needed information are shown in Appendix ??.
+\noindent All SPARQL queries used to gather the needed information are also available at the webpage of this paper.
 
@@
 \item{\textbf{Shanghai Rankings. }} 	
-The page at \cite{rankings} gives an overview of the Shanghai Rankings for 2015.
+The webpage at \cite{rankings} gives an overview of the Shanghai Rankings for 2015. 
 It also includes  information on the criteria used to build this ranking, which includes the awards ranking.
@@
 Because of this, out of all non-linked sources, information from Facebook was by far the easiest to gather.
+One difficulty that is worth mentioning, is the limit of consecutive queries that can be send to the Facebook Graph API.
+We noticed that after sending more or less 630 queries the usertoken that is needed the retrieve the information expires.
+If you generate a new token you aren't allowed to immediatly start querying again.
+You have to wait for at least an hour.
+This is in fact an odd number of queries, if you read the documentation of the Graph API, only 200 queries per hour are allowed \cite{graphAPIlimit}.
 For people with multiple pages, the number of liked for the most liked page is used.
@@
 \subsection{Processing and merging}
-
+\label{ssec:merging}
 After collecting the data from different sources, it has to be combined in some way.

### 2016-01-18 project/paper/appendices/googlescholar.tex
added .latex.yml

\section{Queries}
\lstinputlisting[language=SQL, caption=Query 1]{../queries/allnobelwinners.rq}

### 2016-01-23 project/paper/sections/data.tex
fixed appendices

@@
 In case someone has studied at multiple universities that have a score higher than 0, the average is used.
-Unranked universities automatically have a score of 0 (which is an inherent property of how it is calculated) \todo[inline]{uitleggen wat er gebeurt als er een paar 0 zij}.
+Unranked universities automatically have a score of 0 (which is an inherent property of how it is calculated), if this is the case for someone with multiple universities, then these universities are omitted from the average.
 \item \textbf{Work productivity.} A measure of work productivity can also be useful to include.
@@
 For politicians, the number of speeches they make are perhaps a good indication of how productive they are.
-\emph{Because this is a sensitive subject, Appendix ?A?
-provides a thorough discussion of why we chose these features and how the research question is slightly weakened by our assumption.
+\emph{Because this is a sensitive subject, Appendix \ref{sec:productivity} provides a thorough discussion of why we chose these features and how the research question is slightly weakened by our assumption.
 Furthermore, in Section~\ref{ssec:quality} on quality assessment, we show why we deem both to be a reasonable proxy by comparing their distributions.}
@@
 \noindent All SPARQL queries used to gather the needed information are also available at the webpage of this paper.
+In appendix \ref{sec:data}
 
@@
 A second difficulty arose when Google appeared to block automated requests.
-Appendix ??
-gives an overview of some methods we used in attempt to moderately successfully circumvent those restrictions.
+Appendix \ref{sec:googlescholar} gives an overview of some methods we used in attempt to moderately successfully circumvent those restrictions.
 \end{itemize}

### 2016-01-23 project/paper/appendices/sparql.tex
added appendix C

\section{Linked open data}
\label{sec:lod}
\subsection{Sparql endpoints}
\begin{table}[H]
\centering
\begin{tabular}{l|l}
	\textbf{\textsc{Source}} & \textbf{\textsc{Sparql endpoint}} \\ \hline
	\rule{0pt}{4mm}DBPedia &  \\
	Year of birth & \textbf{DBPedia} \\
	University ranking & \textbf{DBPedia} + Shanghai Ranking 2015\\
	Work Productivity & Google Scholar, \textbf{ToE}\\
	Popularity & Facebook\\
	Nobel Prize& \textbf{Nobelprize.org}
\end{tabular}
\caption{Overview of used features and their respective sources.}
\end{table}
\subsection{Difficulites with LoD}
In this section we discuss our difficulties that we experienced with linked open data (LoD). These are worth mentioning because they influenced our results.

\subsubsection{The language barrier}
The great thing about LoD is that it comes in different languages, what means that you have a bigger and a broader information source.

\subsubsection{LoD is sometimes broken}

### 2016-01-23 project/paper/appendices/sparql.tex
the language barrier

@@
 	\textbf{\textsc{Source}} & \textbf{\textsc{Sparql endpoint}} \\ \hline
-	\rule{0pt}{4mm}DBPedia &  \\
-	Year of birth & \textbf{DBPedia} \\
-	University ranking & \textbf{DBPedia} + Shanghai Ranking 2015\\
-	Work Productivity & Google Scholar, \textbf{ToE}\\
-	Popularity & Facebook\\
-	Nobel Prize& \textbf{Nobelprize.org}
+	\rule{0pt}{4mm}DBPedia & \texttt{http://dbpedia.org/sparql/} \\
+	ToE &  \texttt{http://linkedpolitics.ops.few.vu.nl} \\
+	& \texttt{/sparql/} \\
+	Nobel Prize & \texttt{http://data.nobelprize.org/sparql}
 \end{tabular}
-\caption{Overview of used features and their respective sources.}
+\caption{Overview of used Sparql endpoints.}
 \end{table}
@@
 The great thing about LoD is that it comes in different languages, what means that you have a bigger and a broader information source.
+Unfortunately it also brings a lot of difficulties with it.
+Not only do the names of people, institutions and other features differ from each other, also the arguments that you give in the queries are sometimes spelled differently.
+All these different namings made it more difficult to match the the right names with the right features.
+That's why we decided to filter everything out that wasn't available in English.
+One could say that this would create a bias.
+We decided not to worry about this because the biggest part of LoD is available in English.
 
-\subsubsection{LoD is sometimes broken}
+\subsubsection{It just doesn't work sometimes}

### 2016-01-23 project/paper/appendices/sparql.tex
Byzantine errors

@@
 \subsubsection{It just doesn't work sometimes}
+
+Apart from the language problem there seem to be Byzantine problems that are really weird. We don't have an explation nor a soltion to address these problems.
+
+\begin{enumerate}
+\item \textbf{Links are not broken but queries on them don't work}\\
+Take for example the following person Paul Rübig.
+There is an data item about him on DBpedia:  \url{http://dbpedia.org/page/Paul\_ R\"ubig}.
+But if you query this specific resource with the query in listing \ref{lst:dbpedia} you will not get any results.
+\lstinputlisting[language=SQL, caption=Query that doesn't work, label={lst:dbpedia}]{dbpedia.rq}
+\end{enumerate}

### 2016-01-23 project/scripts/mergeData.pl
Changes.

@@ -2,15 +2,27 @@
 
 use Data::Dumper;
 
-$dFile = "mergedDBpediaNobelNewUni_economist_or_scientist_Final.csv";
+$dFile = "mergedDBpediaNobelNewUni_economist_or_scientist_Final_PARSED.csv";
 $uFile = "rankings_final.csv";
 $lFile = "likes.csv";
 $sFile = "scholarrankings.csv";
+$oFile = "finalData.csv";
 
 %data;              # Main data file
 %rankings;          # University rankings
 %likes;             # Likes
 %scholar;           # Scholar rankings
+
+# Header
+@header = (
+  "Nobel",
+  "Country",
+  "Year",
+  "Type",
+  "UniversityScore",
+  "Productivity",
+  "Popularity"
+);
 
 # READ EVERYTHING
 
@@ -18,7 +30,7 @@ $sFile = "scholarrankings.csv";
 open $dbp, '<', "../data/$dFile";
 while(<$dbp>) {
   chomp;
-  ($name, $year, $country, $university, $type) = split ";", $_;
+  ($name, $year, $country, $university, $type, $nobel) = split ";", $_;
   if (defined $data{$name}) {
     # Already exists, add university.
     push $data{$name}{'university'}, $university;
@@ -28,7 +40,8 @@ while(<$dbp>) {
       year => $year,
       country => $country,
       university => [$university],
-      type => $type
+      type => $type,
+      nobel => $nobel
     };
   }
 }
@@ -60,12 +73,42 @@ while(<$sf>) {
 # MERGE EVERYTHING
 
 foreach $name (keys %data) {
+  # Insert likes and publications
   $data{$name}{'likes'} = $likes{$name};
   $data{$name}{'scholar'} = $scholar{$name};
-  print Dumper($data{$name});
-  last;
+  # University matching
+  $score = 0;
+  $c = 0;
+  foreach $uni (@{$data{$name}{'university'}}) {
+    if ($rankings{$uni} != 0) {
+      $score += $rankings{$uni};
+      $c++;
+    }
+  }
+  if ($score > 0) {
+    $score = $score / $c;
+  }
+  $data{$name}{'score'} = $score;
 }
 
+
+open $out, '>', "../data/$oFile";
+$h = join(";", @header);
+print $out "$h\n";
+foreach $name (keys %data) {
+  @properties = (
+    $data{$name}{'nobel'},
+    $data{$name}{'country'},
[…]

### 2016-01-23 project/scripts/statistics.r

@@ -1,0 +1,52 @@
+nobelAll.df <- read.table('finalData.csv', sep = ';', header = TRUE,  quote = "");
+nobel.df <- na.omit(nobelAll.df)
+
+plot(density(log(nobel.df$Popularity)))
+
+n <- length(nobel.df$Popularity)
+sort(nobel.df$Popularity, partial=n-16)[n-16]
+
+NewPop <- nobel.df$Popularity[which(nobel.df$Popularity < 175000)]
+
+popBp <- boxplot.stats(nobel.df$Popularity, coef = 3)
+summary(popBp)
+plot(popBp)
+
+
+
+nobel.popularity.bp <- boxplot.stats(nobel.df$Popularity)
+plot(density(nobel.df$Popularity, na.rm = TRUE))
+
+par(mfrow = c(2,2))
+by(nobel.df$Productivity, nobel.df$Type, function(x) plot(density(x)))
+by(nobel.df$Popularity, nobel.df$Type, function(x) plot(density(x)))
+
+# Normalise by category
+by(nobel.df$Productivity, nobel.df$Type, function(x) (x / max(x, na.rm = TRUE)));
+by(nobel.df$Popularity, nobel.df$Type, function(x) (x / max(x, na.rm = TRUE)));
+
+# Scholar <- Scholar[rowSums(is.na(Scholar)) == 0,];
+# ScholarRankings <- Scholar$V2;
+# ScholarRankings <- (ScholarRankings - min(ScholarRankings)) / (max(ScholarRankings - min(ScholarRankings)))
+# 
+# Speeches <- read.table('numberofspeeches.csv', sep = ',', header = TRUE, quote = "");
+# SpeechesRankings <- Speeches$count;
+# SpeechesRankings <- (SpeechesRankings - min(SpeechesRankings)) / (max(SpeechesRankings - min(SpeechesRankings)))
+# 
+# boxplot(SpeechesRankings);
+# boxplot(ScholarRankings);
+# 
+# par(mfrow=c(1,2));
+# plot(density(ScholarRankings), main = 'Scholar');
+# plot(density(SpeechesRankings), main = 'Speeches');
+# 
+# # remove outliers
+# x1 <- ScholarRankings[!ScholarRankings %in% boxplot.stats(ScholarRankings)$out];
+# x2 <- SpeechesRankings[!SpeechesRankings %in% boxplot.stats(SpeechesRankings)$out];
+# 
[…]

### 2016-01-23 project/paper/appendices/sparql.tex
Byzantine errors

@@
 But if you query this specific resource with the query in listing \ref{lst:dbpedia} you will not get any results.
-\lstinputlisting[language=SQL, caption=Query that doesn't work, label={lst:dbpedia}]{dbpedia.rq}
+\lstinputlisting[language=SQL, caption=Query that doesn't work, label={lst:dbpedia}]{queries/dbpedia.rq}
+
+\item \textbf{\texttt{dati.camera.it} doesn't work at all}\\
+In the ToE database there are lot of reference to the Italian linked open data source \texttt{dati.camera.it}.
+Unfortunately none of our queries seem to give any result.
+Even not for a really simple one, as you can see in listing \ref{lst:dati}.
+Even though it's link \url{http://dati.camera.it/ocd/persona.rdf/p35360} seems to work fine.
+
+\lstinputlisting[language=SQL, caption=Query that doesn't work on \texttt{dati.camera.it}, label={lst:dati}]{queries/dati.rq}
 \end{enumerate}

### 2016-01-23 project/src/transform_TOE.m
transform_TOE.m

@@ -1,0 +1,92 @@
+% Read the file with the politicians
+fid1 = fopen('ToEdataPoliticiansNotUnique.csv','r','n','UTF-8');
+nbPersons = 125;
+
+names = cell(nbPersons, 1);
+year = cell(nbPersons, 1);
+country = cell(nbPersons, 1);
+university = cell(nbPersons, 1);
+
+tline = fgetl(fid1);
+
+for i=1:nbPersons
+    person_splitted = strsplit(tline,{';'});
+    
+    fullName = strcat(person_splitted{1, 1}, {' '}, person_splitted{1, 2});
+    names{i, 1} = fullName{1};
+    year{i, 1} = person_splitted{1, 3};
+    country{i, 1} = person_splitted{1, 4};
+    university{i, 1} = person_splitted{1, 5};
+
+    tline = fgetl(fid1);
+end
+
+fclose(fid1);
+
+% ADJUST UNIVERSITIES
+% first add a space before and after every university and set to lowercase
+for i=1:nbPersons
+    oldUniversity = university{i, 1};
+    newUniversity = lower(strcat({' '},oldUniversity,{' '}));
+    university{i, 1} = newUniversity{1};
+end
+
+% second remove everything in parentheses
+expression = '\([^)]+\)';
+replace = '';
+
+for i=1:nbPersons
+    oldUniversity = university{i, 1};
+    newUniversity = regexprep(oldUniversity,expression,replace);
+    university{i, 1} = newUniversity;
+end
+
+% next remove all punctuation
+for i=1:nbPersons
+    oldUniversity = university{i, 1};
+    newUniversity = strrep(strrep(strrep(strrep(strrep(strrep(oldUniversity, ',', ''), '.', ''), '(', ''), ')', ''), '''', ''), '-', '');
+    university{i, 1} = newUniversity;
+end
+
+% then remove the words university, college, state, of, the 
+% and remove the white spaces before and after again
+for i=1:nbPersons
+    oldUniversity = university{i, 1};
+    newUniversity = strrep(strrep(strrep(strrep(strrep(oldUniversity, ' university ', ' '), ' college ', ' '), ' state ', ' '), ' of ', ' '), ' the ', ' ');
+    university{i, 1} = strtrim(newUniversity);
+end
+
+% lastly remove all the white spaces
+for i=1:nbPersons
+    oldUniversity = university{i, 1};
[…]

### 2016-01-23 project/src/transform2.m
Create transform2.m

@@ -1,0 +1,94 @@
+% Read the file with the persons
+fid1 = fopen('mergedDBpediaNobelNewUni_economist_or_scientist_Final.csv','r','n','UTF-8');
+nbPersons = 10987;
+
+names = cell(nbPersons, 1);
+year = cell(nbPersons, 1);
+country = cell(nbPersons, 1);
+university = cell(nbPersons, 1);
+category = cell(nbPersons, 1);
+nobel = cell(nbPersons, 1);
+
+tline = fgetl(fid1);
+
+for i=1:nbPersons
+    person_splitted = strsplit(tline,{';'});
+    
+    names{i, 1} = person_splitted{1, 1};
+    year{i, 1} = person_splitted{1, 2};
+    country{i, 1} = person_splitted{1, 3};
+    university{i, 1} = person_splitted{1, 4};
+    category{i, 1} = person_splitted{1, 5};
+    nobel{i, 1} = person_splitted{1, 6};
+
+    tline = fgetl(fid1);
+end
+
+fclose(fid1);
+
+% ADJUST UNIVERSITIES
+% first add a space before and after every university and set to lowercase
+for i=1:nbPersons
+    oldUniversity = university{i, 1};
+    newUniversity = lower(strcat({' '},oldUniversity,{' '}));
+    university{i, 1} = newUniversity{1};
+end
+
+% second remove everything in parentheses
+expression = '\([^)]+\)';
+replace = '';
+
+for i=1:nbPersons
+    oldUniversity = university{i, 1};
+    newUniversity = regexprep(oldUniversity,expression,replace);
+    university{i, 1} = newUniversity;
+end
+
+% next remove all punctuation
+for i=1:nbPersons
+    oldUniversity = university{i, 1};
+    newUniversity = strrep(strrep(strrep(strrep(strrep(strrep(oldUniversity, ',', ''), '.', ''), '(', ''), ')', ''), '''', ''), '-', '');
+    university{i, 1} = newUniversity;
+end
+
+% then remove the words university, college, state, of, the 
+% and remove the white spaces before and after again
+for i=1:nbPersons
+    oldUniversity = university{i, 1};
+    newUniversity = strrep(strrep(strrep(strrep(strrep(oldUniversity, ' university ', ' '), ' college ', ' '), ' state ', ' '), ' of ', ' '), ' the ', ' ');
+    university{i, 1} = strtrim(newUniversity);
+end
+
[…]

### 2016-01-23 project/paper/figures/popuInitialBox.tex
Model. Figures for statistics.

% Created by tikzDevice version 0.9 on 2016-01-23 15:17:08
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (505.89,505.89);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (480.69,456.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.2pt,line join=round] (185.04, 75.85) -- (344.85, 75.85);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (264.94, 75.85) -- (264.94, 75.85);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (264.94, 75.85) -- (264.94, 75.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.99, 75.85) -- (304.90, 75.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.99, 75.85) -- (304.90, 75.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.04, 75.85) --
	(344.85, 75.85) --
	(344.85, 75.85) --
	(185.04, 75.85) --
	(185.04, 75.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 77.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,115.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 78.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 77.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,101.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 80.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 83.75) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,109.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 88.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 77.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,142.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 90.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 78.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.21) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 77.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 81.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 79.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.61) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 99.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 82.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 80.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,442.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 97.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 77.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 78.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,141.61) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 81.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 76.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94, 75.87) circle (  2.25);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,505.89);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 75.85) -- ( 49.20,391.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 75.85) -- ( 43.20, 75.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,181.03) -- ( 43.20,181.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,286.21) -- ( 43.20,286.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,391.39) -- ( 43.20,391.39);

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80, 75.85) {0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,181.03) {$5 \times 10^6$};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,286.21) {$10^7$};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,391.39) {$1.5 \times 10^7$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 61.20) --
	(480.69, 61.20) --
	(480.69,456.69) --
	( 49.20,456.69) --
	( 49.20, 61.20);
\end{scope}
\end{tikzpicture}

\end{document}

### 2016-01-23 project/paper/figures/popuTransformedBox.tex
Model. Figures for statistics.

% Created by tikzDevice version 0.9 on 2016-01-23 15:12:57
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (505.89,505.89);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (480.69,456.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.2pt,line join=round] (185.04,118.59) -- (344.85,118.59);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (264.94, 75.85) -- (264.94, 75.85);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (264.94,292.73) -- (264.94,162.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.99, 75.85) -- (304.90, 75.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.99,292.73) -- (304.90,292.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.04, 75.85) --
	(344.85, 75.85) --
	(344.85,162.63) --
	(185.04,162.63) --
	(185.04, 75.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,325.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,393.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,332.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,294.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,302.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,329.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,383.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,347.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,357.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,308.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,312.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,389.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,307.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,367.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,297.76) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,294.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,312.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,308.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,323.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,404.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,299.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,371.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,329.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,295.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,304.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,297.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,314.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,326.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,352.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,297.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,301.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,297.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,341.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,300.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,306.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,382.30) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,354.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,309.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,343.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,442.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,379.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,323.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,333.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,302.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,298.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,301.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,404.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,306.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,305.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,350.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,295.43) circle (  2.25);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,505.89);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 75.85) -- ( 49.20,405.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 75.85) -- ( 43.20, 75.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,185.67) -- ( 43.20,185.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,295.49) -- ( 43.20,295.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,405.31) -- ( 43.20,405.31);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 37.20, 72.40) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 37.20,182.22) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 37.20,292.04) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 37.20,401.87) {15};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 61.20) --
	(480.69, 61.20) --
	(480.69,456.69) --
	( 49.20,456.69) --
	( 49.20, 61.20);
\end{scope}
\end{tikzpicture}

\end{document}

### 2016-01-23 project/paper/figures/prodInitialBox.tex
Model. Figures for statistics.

% Created by tikzDevice version 0.9 on 2016-01-23 19:46:20
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (505.89,505.89);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (480.69,456.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.2pt,line join=round] (185.04,109.27) -- (344.85,109.27);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (264.94, 75.85) -- (264.94, 82.09);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (264.94,282.27) -- (264.94,162.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.99, 75.85) -- (304.90, 75.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.99,282.27) -- (304.90,282.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.04, 82.09) --
	(344.85, 82.09) --
	(344.85,162.16) --
	(185.04,162.16) --
	(185.04, 82.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,364.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,285.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,364.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,284.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,289.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,336.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,339.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,397.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,305.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,360.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,432.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,380.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,305.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,288.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,324.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,329.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,306.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,315.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,408.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,290.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,353.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,301.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,388.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,433.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,289.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,298.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,372.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,399.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,289.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,309.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,322.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,328.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,342.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,307.61) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,315.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,295.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,380.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,323.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,303.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,312.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,395.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,296.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,284.84) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,295.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,291.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,362.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,320.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,381.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,373.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,370.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,394.66) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,324.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,437.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,361.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,327.81) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,324.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,326.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,344.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,393.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,417.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,376.66) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,424.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,369.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,365.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,399.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,350.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,351.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,310.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,337.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,288.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,303.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,290.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,410.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,295.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,397.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,292.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,328.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,301.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,308.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,339.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,422.21) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,330.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,380.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,299.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,299.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,350.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,327.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,345.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,416.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,414.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,394.66) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,296.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,290.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,329.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,334.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,338.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,379.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,310.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,352.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,312.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,327.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,332.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,436.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,333.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,293.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,368.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,321.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,334.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,418.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,341.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,322.30) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,290.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,356.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,293.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,362.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,369.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,363.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,354.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,331.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,287.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,284.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,392.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,400.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,309.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,295.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,325.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,380.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,370.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,434.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,384.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,317.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,396.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,311.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,361.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,426.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,283.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,305.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,399.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,317.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,367.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,338.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,327.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,411.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,427.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,320.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,299.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,317.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,371.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,298.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,397.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,351.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,341.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,307.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,403.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,430.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,333.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,328.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,413.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,324.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,342.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,421.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,346.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,354.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,411.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,339.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,441.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,325.24) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,287.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,335.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,304.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,342.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,291.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,287.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,283.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,325.24) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,299.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,294.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,297.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,299.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,366.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,402.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,359.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,297.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,380.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,312.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,324.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,317.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,305.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,320.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,333.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,422.21) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,363.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,343.61) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,284.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,309.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,307.61) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,401.27) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,316.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,284.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,348.75) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,314.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,415.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,328.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,427.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,302.84) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,306.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,315.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,357.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,334.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,298.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,372.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,395.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,319.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,311.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,314.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,288.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,292.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,348.75) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,298.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,378.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,418.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,378.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,373.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,290.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,349.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,438.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,312.75) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,325.24) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,320.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,282.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,353.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,288.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,286.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,386.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,312.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,429.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,283.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,290.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,438.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,326.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,336.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,346.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,421.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,390.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,406.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,363.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,318.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,318.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,306.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,287.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,314.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,286.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,297.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,311.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,313.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,324.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,338.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,371.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,332.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,295.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,323.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,345.81) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,350.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,405.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,400.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,392.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,356.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,310.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,339.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,403.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,368.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,391.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,366.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,297.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,431.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,354.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,339.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,344.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,284.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,311.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,339.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,372.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,322.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,334.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,364.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,307.24) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,322.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,298.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,297.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,304.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,290.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,357.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,435.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,339.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,342.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,334.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,326.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,289.61) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,441.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,388.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,310.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,309.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,418.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,300.27) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,320.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,442.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,330.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,338.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,354.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,342.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,288.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,370.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,302.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,366.75) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,367.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,347.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,299.53) circle (  2.25);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,505.89);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 75.85) -- ( 49.20,443.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 75.85) -- ( 43.20, 75.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,149.31) -- ( 43.20,149.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,222.77) -- ( 43.20,222.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,296.23) -- ( 43.20,296.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,369.68) -- ( 43.20,369.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,443.14) -- ( 43.20,443.14);

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80, 75.85) {0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,149.31) {200};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,222.77) {400};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,296.23) {600};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,369.68) {800};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,443.14) {1000};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 61.20) --
	(480.69, 61.20) --
	(480.69,456.69) --
	( 49.20,456.69) --
	( 49.20, 61.20);
\end{scope}
\end{tikzpicture}

\end{document}

### 2016-01-23 project/scripts/statistics.r

@@ -1,52 +1,86 @@
+library(tikzDevice)
+library(plyr)
+
+# Read file
 nobelAll.df <- read.table('finalData.csv', sep = ';', header = TRUE,  quote = "");
+# Remove missing values
 nobel.df <- na.omit(nobelAll.df)
 
-plot(density(log(nobel.df$Popularity)))
+##############
+# POPULARITY #
+##############
 
-n <- length(nobel.df$Popularity)
-sort(nobel.df$Popularity, partial=n-16)[n-16]
-
-NewPop <- nobel.df$Popularity[which(nobel.df$Popularity < 175000)]
-
-popBp <- boxplot.stats(nobel.df$Popularity, coef = 3)
-summary(popBp)
-plot(popBp)
-
-
-
-nobel.popularity.bp <- boxplot.stats(nobel.df$Popularity)
-plot(density(nobel.df$Popularity, na.rm = TRUE))
-
-par(mfrow = c(2,2))
-by(nobel.df$Productivity, nobel.df$Type, function(x) plot(density(x)))
-by(nobel.df$Popularity, nobel.df$Type, function(x) plot(density(x)))
-
-# Normalise by category
-by(nobel.df$Productivity, nobel.df$Type, function(x) (x / max(x, na.rm = TRUE)));
-by(nobel.df$Popularity, nobel.df$Type, function(x) (x / max(x, na.rm = TRUE)));
-
-# Scholar <- Scholar[rowSums(is.na(Scholar)) == 0,];
-# ScholarRankings <- Scholar$V2;
-# ScholarRankings <- (ScholarRankings - min(ScholarRankings)) / (max(ScholarRankings - min(ScholarRankings)))
+# # Boxplot of popularity
+# tikz('../paper/figures/initialBox.tex', standAlone = TRUE)
+# boxplot(nobel.df$Popularity, axes = F)
+# axis(2,
+#      at = c(0, 5e+06,              1e+07,    1.5e+07),
+#  labels = c(0, "$5 \\times 10^6$", "$10^7$", "$1.5 \\times 10^7$"))
+# box()
+# dev.off()
 # 
-# Speeches <- read.table('numberofspeeches.csv', sep = ',', header = TRUE, quote = "");
-# SpeechesRankings <- Speeches$count;
-# SpeechesRankings <- (SpeechesRankings - min(SpeechesRankings)) / (max(SpeechesRankings - min(SpeechesRankings)))
+# # Density plot of popularity
[…]

### 2016-01-26 project/paper/appendices/sparql.tex
future work
typfouten verbeterd

@@
+\pagebreak
 \section{Linked open data}
@@
 \end{table}
-\subsection{Difficulites with LoD}
-In this section we discuss our difficulties that we experienced with linked open data (LoD). These are worth mentioning because they influenced our results.
+\subsection{Difficulties with LoD}
+In this section we discuss the difficulties that we experienced with linked open data (LoD). These are worth mentioning because they influenced our results.
 
@@
 Not only do the names of people, institutions and other features differ from each other, also the arguments that you give in the queries are sometimes spelled differently.
-All these different namings made it more difficult to match the the right names with the right features.
+All these different namings made it more difficult to match the right names with the right features.
 That's why we decided to filter everything out that wasn't available in English.
@@
 
-Apart from the language problem there seem to be Byzantine problems that are really weird. We don't have an explation nor a soltion to address these problems.
+Apart from the language problem there seem to be Byzantine problems that are really weird. We don't have an explanation nor a solution to address these problems.
 
@@
 \item \textbf{Links are not broken but queries on them don't work}\\
-Take for example the following person Paul Rübig.
-There is an data item about him on DBpedia:  \url{http://dbpedia.org/page/Paul\_ R\"ubig}.
+Take for example the person Paul R\"ubig.
+There is an data item about him on DBpedia: http://dbpedia.org/page/Paul\_R\"ubig.
 But if you query this specific resource with the query in listing \ref{lst:dbpedia} you will not get any results.
@@
 Unfortunately none of our queries seem to give any result.
-Even not for a really simple one, as you can see in listing \ref{lst:dati}.
-Even though it's link \url{http://dati.camera.it/ocd/persona.rdf/p35360} seems to work fine.
+Even not for a really simple one, as you can see in listing \ref{lst:dati} and this even though its link \url{http://dati.camera.it/ocd/persona.rdf/p35360} seems to work fine.
 

### 2016-01-26 project/paper/sections/data.tex
appendices

@@
 \begin{itemize}
-\item \textbf{Year and data of birth.}
+\item \textbf{Year and country of birth.}
 Currently the average age of a laureate is 59 \cite{age}.
@@
 For example, young scientists are far less likely to win an award because they have yet to prove themselves.
+Next to this, we are also interested to see if the country of a person has an influence on this.
 \item \textbf{Alma mater.} We suppose that there's a link between the university where one graduated and his chances of winning a Nobel Prize.
@@
 Although it can be edited by anyone, data correctness is verified thoroughly by a team of content moderators.
-For this reason we get a large part of our training set data from DBpedia.
+For this reason we get a large part of our training dataset from DBpedia.
 More specifically, we retrieve the year and country of birth, as well as alma mater and of course their full name.
@@
 \noindent All SPARQL queries used to gather the needed information are also available at the webpage of this paper.
-In appendix \ref{sec:data}
+In appendix \ref{sec:lod} we provide the links to the specific endpoints and also some of our experiences of using Linked Open Data.
 
@@
 Universities that are not listed have an award ranking of 0.
-Because of tabular form, retrieving the data was fairly straightforward.
+Because of the tabular form, retrieving the data was fairly straightforward.
 
@@
 One difficulty that is worth mentioning, is the limit of consecutive queries that can be send to the Facebook Graph API.
-We noticed that after sending more or less 630 queries the usertoken that is needed the retrieve the information expires.
+We noticed that after sending more or less 630 queries, the user token that is needed to retrieve the information expires.
 If you generate a new token you aren't allowed to immediatly start querying again.
@@
 This is in fact an odd number of queries, if you read the documentation of the Graph API, only 200 queries per hour are allowed \cite{graphAPIlimit}.
-For people with multiple pages, the number of liked for the most liked page is used.
+For people with multiple pages, the number of likes for the most liked page is used.
 Because popular names might have pages not related to the scientist we are interested in, some results might be noisy.
@@
 The hardest part was matching universities from DBPedia to those retrieved by scraping the ARWU rankings.
+We used a fuzzy matcher that used ... ...
+\todo[inline]{Gust of Katrien, wie had hier nu juist de matching gedaan?, ik ken in ider geval de details niet}

### 2016-01-26 project/paper/sections/analysis.tex
Verslag enzuu

@@
 
+In this section we first perform an initial analysis of the data.
+We check their distributions and assess whether transformations should be performed for better expected results.
+Furthermore, we can get an initial idea of what variables will perform well by comparing the mean values for people with and without a Nobel Prize.
+This analysis is done using the R statistical software package.
+
+Next, the logistic regression model is learned on the resulting dataset and evaluated using cross-validation.
+We experiment with excluding variables that are not relevant and balancing the number of positive and negative examples.
+
 \subsection{Quality assessment}
 \label{ssec:quality}
-\todo[inline]{Alinea over hoe we data samen zetten.
-Name matching, problemen hierbij, Aantal entries in training dataset en research set, aantal positieve voorbeelden t.o.v.
-negatieve voorbeelden (en vermelden dat dit een probleem is en hoe we dit oplossen/compenseren), andere statistieken i.v.m.
-data, outliers}
+
+The merged dataset contains two variables that are \emph{fuzzy}: the number of likes on Facebook, which serves as a popularity measure, and the number of results for a specialised Google Scholar search, which serves as a productivity measure.
+Both might be prone to errors.
+Furthermore, some normalisation should be performed so that variables with a larger scale do not receive more weight in the final model.
+Since the university rankings are on a scale of $[0, 100]$ we will transform all variables to that scale.
+
+\subsubsection{Popularity measure}
+\label{sssec:popularity}
+The popularity measure comes from gathering the number of likes on Facebook.
+Because this is done automatically and popular names might occur more than ones, we should check for outliers.
+A boxplot is shown in Figure~\ref{fig:popuInitialBox} and a density plot in Figure~\ref{fig:popuInitialDensity}.
+We can immediately see a problem: the outlier at 17 million deforms the distribution.
+It is the result for Einstein, however, and not an error in the data.
+Manual verification confirmed this for all seemingly high values.
+In order to solve this without having to remove any data, we perform a transformation using the natural logarithm.
+Logarithmic transformations are often used to normalise right-skewed distributions.
+The exact transformation is given by
+\begin{equation}
+\label{eq:logtransform}
+t(x) = \begin{cases} ln(x), & \mbox{if } x \neq 0 \\ 0, & \mbox{if } x = 0 \end{cases}
+\end{equation}
+in order to correct $ln(0) = -\infty$.
+The same plots for the resulting distribution are given in Figures~\ref{fig:popuTransformedBox} and \ref{fig:popuTransformedDensity}.
+While still being far from normal, the outliers are now far less extreme.
+Next, the results are normalised by dividing by the maximal value and rescaled to $[0, 100]$.
+
+In order to get an initial estimate whether it will be significant in the model, we can compare the mean value for winners and non-winners.
+Since there are sufficient examples, we may assume normality of sampling distributions and perform a standard two-sample $t$ test for unequal variances.
+The sample means are
+\begin{table}[H]
+\centering
+\begin{tabular}{c|c}
+\textbf{\textsc{Nobel}} & \textbf{\textsc{Non-nobel}} \\ \hline
+\rule{0pt}{4mm}23.05663&14.44544\\
+\end{tabular}
+\end{table}
+Using R we find that the true means are not equal, which is what we hoped for the model.
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.4\textwidth}
+        \includegraphics[width=\textwidth]{figures/popuInitialBox.pdf}
+        \caption{Boxplot}
+        \label{fig:popuInitialBox}
+    \end{subfigure}
+    ~
+    \begin{subfigure}[b]{0.4\textwidth}
+        \includegraphics[width=\textwidth]{figures/popuInitialDensity}
+        \caption{Density plot}
+        \label{fig:popuInitialDensity}
+    \end{subfigure}
+    \caption{Distribution plots for raw popularity measure.}
+\end{figure*}
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.4\textwidth}
+        \includegraphics[width=\textwidth]{figures/popuTransformedBox}
+        \caption{Boxplot}
+        \label{fig:popuTransformedBox}
+    \end{subfigure}
+    ~
+    \begin{subfigure}[b]{0.4\textwidth}
+        \includegraphics[width=\textwidth]{figures/popuTransformedDensity}
+        \caption{Density plot}
+        \label{fig:popuTransformedDensity}
+    \end{subfigure}
+    \caption{Distribution plots for transformed popularity measure.}
+\end{figure*}
+
+\subsubsection{Productivity measure}
+\label{sssec:productivity}
 

### 2016-01-26 project/paper/sections/data.tex
Verslag enzuu

--- 2016-01-23 project/paper/sections/data.tex
@@
 Because of this, out of all non-linked sources, information from Facebook was by far the easiest to gather.
+
 One difficulty that is worth mentioning, is the limit of consecutive queries that can be send to the Facebook Graph API.
-We noticed that after sending more or less 630 queries the usertoken that is needed the retrieve the information expires.
-If you generate a new token you aren't allowed to immediatly start querying again.
-You have to wait for at least an hour.
-This is in fact an odd number of queries, if you read the documentation of the Graph API, only 200 queries per hour are allowed \cite{graphAPIlimit}.
+We noticed that after sending more or less 630 queries the user token that is needed to retrieve information expires.
+If you generate a new token, you aren't allowed to immediately start querying again but have to wait half an hour.
+This number of queries is odd, the Graph API documentation states that only 200 queries per hour are allowed \cite{graphAPIlimit}.
+
 For people with multiple pages, the number of liked for the most liked page is used.
@@
 However, as before, people with the same name can give noisy results, so some outlier detection has to be performed.
-A second difficulty arose when Google appeared to block automated requests.
+An additional difficulty arose when Google appeared to block automated requests.
 Appendix \ref{sec:googlescholar} gives an overview of some methods we used in attempt to moderately successfully circumvent those restrictions.

### 2016-01-26 project/scripts/statistics.r

@@ -6,6 +6,10 @@ nobelAll.df <- read.table('finalData.csv', sep = ';', header = TRUE,  quote = ""
 # Remove missing values
 nobel.df <- na.omit(nobelAll.df)
 
+# Number of positive and negative
+sum(nobel.df$Nobel == "yes")
+sum(nobel.df$Nobel == "no")
+
 ##############
 # POPULARITY #
 ##############
@@ -49,9 +53,13 @@ nobel.df$LogPopularityStand <- ave(nobel.df$LogPopularity,
                                    nobel.df$Type, 
                                    FUN = function(x) x / max(x))
 
+var.test(nobel.df$LogPopularityStand[nobel.df$Nobel == "yes"],
+         nobel.df$LogPopularityStand[nobel.df$Nobel == "no"])
+
 # Test if there is sufficient difference in means
 t.test(nobel.df$LogPopularityStand[nobel.df$Nobel == "yes"],
-       nobel.df$LogPopularityStand[nobel.df$Nobel == "no"])
+       nobel.df$LogPopularityStand[nobel.df$Nobel == "no"],
+       var.equal = FALSE)
 # Luckily -> yes.
 
 ################

### 2016-01-26 project/paper/appendices/productivity.tex
fixed appendices

@@
 \section{Discussion on work productivity}
+\label{sec:productivity}
 
@@
 Since a politician isn't eligible to receive such prize, we can't use them as negative examples.
-It is thus inevitable to use different examples in the training set and the testing set.
+It is thus inevitable to use different examples in the training dataset and the research dataset.
 
@@
 For speeches the same happens, where a lot of speeches might just as well mean that a politician is only talking, without actually \emph{doing} much.
-This re\"inforces our belief that both might be a good proxy for the same feature.
+This reinforces our belief that both might be a good proxy for the same feature.
 

### 2016-01-26 project/paper/sections/methodology.tex

@@
 This can be used to learn a predictive model.
-The research data set contains the same features, but then for politicians for which we would like to answer the research question.
-\item Some statistics are applied to the training data to assess its quality. For example, because collecting the data is prone to errors, some outlier detection and removal has to be perfomed.
+The research dataset contains the same features, but then for politicians for which we would like to answer the research question.
+\item Some statistics are applied to the training data to assess its quality. For example, because collecting the data is prone to errors, some outlier detection and removal has to be performed.
 \item The final training dataset is used to learn a model that is able to predict how likely a person is to win a Nobel Prize.
@@
 The model's accuracy is assessed using cross-validation on the training dataset.
-\item The final step is applying the learned model on the training dataset and discussing its results. 
+\item The final step is applying the learned model on the research dataset and discussing the results. 
 \end{enumerate}

### 2016-01-26 project/paper/figures/prodNoOutBox.tex
Verslag update.

% Created by tikzDevice version 0.9 on 2016-01-26 14:06:46
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (505.89,505.89);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (480.69,456.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.2pt,line join=round] (185.04,127.32) -- (344.85,127.32);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (264.94, 75.85) -- (264.94, 85.62);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (264.94,393.17) -- (264.94,208.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.99, 75.85) -- (304.90, 75.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.99,393.17) -- (304.90,393.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.04, 85.62) --
	(344.85, 85.62) --
	(344.85,208.77) --
	(185.04,208.77) --
	(185.04, 85.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,393.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,397.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,423.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,428.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,410.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,400.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,395.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,414.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,406.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,415.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,417.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,410.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,433.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,407.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,415.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,415.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,399.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,402.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,404.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,394.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,436.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,422.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,402.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,402.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,410.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,405.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,440.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,414.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,430.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,415.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,404.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,434.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,438.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,401.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,407.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,413.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,425.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,402.30) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,425.75) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,415.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,408.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,421.84) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,427.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,400.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,405.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,414.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,437.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,398.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,420.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,423.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,406.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,404.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,411.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,418.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,436.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,440.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,413.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,407.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,425.75) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,398.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,407.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,428.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,424.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,402.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,417.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,411.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,404.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,412.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,405.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,431.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,440.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,417.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,415.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,408.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,410.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,394.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,420.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,416.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,421.84) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,412.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,420.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,408.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,394.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,410.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,437.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,402.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,423.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,433.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,399.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,414.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,432.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,404.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,417.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,397.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,422.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,412.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,398.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,439.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,428.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,423.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,417.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,410.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,397.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,431.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,418.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,418.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,429.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,400.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,434.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,413.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,439.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,399.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,424.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,429.66) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,436.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,404.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,403.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,412.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,421.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,408.81) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,421.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,410.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,436.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,416.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,407.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,400.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,435.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,441.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,412.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,438.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,438.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,432.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,442.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,434.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,415.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.94,402.95) circle (  2.25);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,505.89);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 75.85) -- ( 49.20,401.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 75.85) -- ( 43.20, 75.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,141.01) -- ( 43.20,141.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,206.17) -- ( 43.20,206.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,271.33) -- ( 43.20,271.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,336.48) -- ( 43.20,336.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,401.64) -- ( 43.20,401.64);

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80, 75.85) {0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,141.01) {100};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,206.17) {200};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,271.33) {300};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,336.48) {400};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,401.64) {500};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 61.20) --
	(480.69, 61.20) --
	(480.69,456.69) --
	( 49.20,456.69) --
	( 49.20, 61.20);
\end{scope}
\end{tikzpicture}

\end{document}

### 2016-01-26 project/paper/sections/analysis.tex
Verslag update.

@@
 \end{table} 
-Using R we find that the true means are not equal, which is what we hoped for the model.
+\noindent Using R we find that the true means are not equal with confidence level $0.05$, which is what we hoped for the model.
 \begin{figure*}
     \centering
-    \begin{subfigure}[b]{0.4\textwidth}
+    \begin{subfigure}[b]{0.3\textwidth}
         \includegraphics[width=\textwidth]{figures/popuInitialBox.pdf}
@@
     \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.4\textwidth}
+    \quad
+    \begin{subfigure}[b]{0.3\textwidth}
         \includegraphics[width=\textwidth]{figures/popuInitialDensity}
@@
     \centering
-    \begin{subfigure}[b]{0.4\textwidth}
+    \begin{subfigure}[b]{0.3\textwidth}
         \includegraphics[width=\textwidth]{figures/popuTransformedBox}
@@
     \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.4\textwidth}
+    \quad
+    \begin{subfigure}[b]{0.3\textwidth}
         \includegraphics[width=\textwidth]{figures/popuTransformedDensity}
@@
 \label{sssec:productivity}
+The productivity measure does have outliers, because searching Google Scholar is always a fuzzy search.
+For example, searching for "Edgar Allen" gives us a result of 996 publications, which is  probably an overestimate.
+In order to remove these, we perform standard outlier detection, so we remove all points that lie beyond the extremes of the whiskers.
+The whiskers are extended to 1.5 times the length of the boxes in the boxplot.
+A density plot of before and after removing the outliers is shown in Figure~\ref{fig:productivity}.
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{figures/prodInitialDensity.pdf}
+        \caption{Before outlier removal}
+        \label{fig:prodInitialDensity}
+    \end{subfigure}
+    \quad
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{figures/prodNoOutDensity}
+        \caption{After removing outliers}
+        \label{fig:prodNoOutDensity}
+    \end{subfigure}
+    \caption{Density plots for productivity measure.}
+    \label{fig:productivity}
+\end{figure*}
+
+After removing outliers, we rescale the data to $[0, 100]$ per category. The resulting means are given below.
+\begin{table}[H]
+\centering
+\begin{tabular}{c|c}
+\textbf{\textsc{Nobel}} & \textbf{\textsc{Non-nobel}} \\ \hline
+\rule{0pt}{4mm}25.30257&22.79697 \\
+\end{tabular}
+\end{table}
+\noindent Yet again, we test for equality of means and find that they are not equal, however this time only slightly ($p = 0.03971$, only slightly smaller than the default confidence level $0.05$).
+Note that before removing outliers they were equal according to the test, which supports our decision to remove outliers.
 
@@
 
-\todo[inline]{figuren hier ter visualisatie data}
-
 \todo[inline]{Sectie over difficulties (training data veel negatieve en weinig positieve examples, links die er niet zijn}

### 2016-01-26 project/scripts/statistics.r

@@ -51,7 +51,7 @@ nobel.df$LogPopularity[nobel.df$LogPopularity == -Inf] <- 0
 # Standardise by category
 nobel.df$LogPopularityStand <- ave(nobel.df$LogPopularity, 
                                    nobel.df$Type, 
-                                   FUN = function(x) x / max(x))
+                                   FUN = function(x) (x / max(x)) * 100)
 
 var.test(nobel.df$LogPopularityStand[nobel.df$Nobel == "yes"],
          nobel.df$LogPopularityStand[nobel.df$Nobel == "no"])
@@ -74,15 +74,23 @@ t.test(nobel.df$LogPopularityStand[nobel.df$Nobel == "yes"],
 # plot(density(nobel.df$Productivity))
 # dev.off()
 
+prod.stats <- boxplot.stats(nobel.df$Productivity)
+length(prod.stats$out)
+
+# Remove outliers
+nobel.df <- nobel.df[!nobel.df$Productivity %in% prod.stats$out,]
+
 # Normalise popularity by category
 nobel.df$ProductivityStand <- ave(nobel.df$Productivity, 
                                   nobel.df$Type, 
-                                  FUN = function(x) x / max(x))
+                                  FUN = function(x) (x / max(x)) * 100)
 
 # Verify whether the means are different
 t.test(nobel.df$ProductivityStand[nobel.df$Nobel == "yes"],
-       nobel.df$ProductivityStand[nobel.df$Nobel == "no"])
+       nobel.df$ProductivityStand[nobel.df$Nobel == "no"],
+       var.equal = FALSE)
 # Luckily -> yes (although only slightly).
+
 
 # Save resulting files
 variables <- c("Nobel", "Country", "Year", "UniversityScore", 

### 2016-01-26 project/paper/sections/data.tex

@@
 For the most part, this was pretty easy by matching names.
-The hardest part was matching universities from DBPedia to those retrieved by scraping the ARWU rankings.
-We used a fuzzy matcher that used ... ...
-\todo[inline]{Gust of Katrien, wie had hier nu juist de matching gedaan?, ik ken in ider geval de details niet}
+The hardest part was matching the universities of the people with those in the Shanghai rankings to retrieve the correct ranking score.
+We discuss how we did this in subsection 2.5.1.
+Another difficulty was getting the universities for the Nobel Prize winners. More on this issue can be found in subsection 2.5.2.
+We also performed a small transformation on the countries, as explained in subsection 2.5.3.
+
+\subsubsection{Matching of universities}
+Not all the universities of the people (found on DBpedia) were an exact match with some university from the Shanghai rankings.
+When taking a closer look at these, we discovered that some of them actually were in the list of Shanghai rankings, but with different spelling.
+For this reason, we first applied some transformations on both the universities of the people and those from the Shangai rankings before matching them.
+These transformations include : setting everything to lowercase, removing everything in parentheses, removing all punctuation, removing the words 'university', 'college', 'state', 'of' and 'the' and removing all white spaces.
+Universities which still not can be found in this way are just expected to have a ranking score of 0.
+
+\subsubsection{Getting the universities for the Nobel Prize winners}
+
+Another problem we encountered was while getting the universities for the Nobel Prize winners.
+Nobelprize.org does not contain the alma mater for the Nobel Prize winners.
+Instead, they store the unversity or research institution the Nobel Prize winner was affiliated with when winning the prize.
+For this reason we had to get the alma maters for the Nobel Prize winners from DBpedia.
+As Nobelprize.org does not have a \textit{sameAs} link with DBpedia, this also has to be done with simple name matching on the first and last name of the Nobel Prize winner.
+However, DBpedia does not have an alma mater for 580 out of the total of 866 Nobel Prize winners.
+Since we already have to deal with a situation in which we have a lot of negative examples and a few positive examples, we want to use as many Nobel Prize winners as possible.
+For this reason, we settled for the universities stored on Nobelprize.org for all Nobel Prize winners for whom we could not find their alma mater on DBpedia.
+However, there are still 191 Nobel Prize winners for whom we could not find a university both on DBpedia and Nobelprize.org and that we omit for this reason.
+
+\subsubsection{Transforming the countries}
+
+We noticed that some Nobel Prize winners had as a country something like 'Germany (now Poland)'.
+For this reason, we transformed the countries so that everything between parentheses gets removed.
+We also set all countries to lowercase.

### 2016-01-26 project/paper/sections/data.tex
zonder country

@@
 \begin{itemize}
-\item \textbf{Year and country of birth.}
+\item \textbf{Year of birth.}
 Currently the average age of a laureate is 59 \cite{age}.
@@
 For example, young scientists are far less likely to win an award because they have yet to prove themselves.
-Next to this, we are also interested to see if the country of a person has an influence on this.
 \item \textbf{Alma mater.} We suppose that there's a link between the university where one graduated and his chances of winning a Nobel Prize.
@@
 For this reason we get a large part of our training dataset from DBpedia.
-More specifically, we retrieve the year and country of birth, as well as alma mater and of course their full name.
+More specifically, we retrieve the year of birth, as well as alma mater and of course their full name.
 The name mostly serves as an identifier for linking data from multiple sources.
@@
 Because of this, out of all non-linked sources, information from Facebook was by far the easiest to gather.
-
 One difficulty that is worth mentioning, is the limit of consecutive queries that can be send to the Facebook Graph API.
-We noticed that after sending more or less 630 queries the user token that is needed to retrieve information expires.
-If you generate a new token, you aren't allowed to immediately start querying again but have to wait half an hour.
-This number of queries is odd, the Graph API documentation states that only 200 queries per hour are allowed \cite{graphAPIlimit}.
-
-For people with multiple pages, the number of liked for the most liked page is used.
+We noticed that after sending more or less 630 queries, the user token that is needed to retrieve the information expires.
+If you generate a new token you aren't allowed to immediatly start querying again.
+You have to wait for at least an hour.
+This is in fact an odd number of queries, if you read the documentation of the Graph API, only 200 queries per hour are allowed \cite{graphAPIlimit}.
+For people with multiple pages, the number of likes for the most liked page is used.
 Because popular names might have pages not related to the scientist we are interested in, some results might be noisy.
@@
 However, as before, people with the same name can give noisy results, so some outlier detection has to be performed.
-An additional difficulty arose when Google appeared to block automated requests.
+A second difficulty arose when Google appeared to block automated requests.
 Appendix \ref{sec:googlescholar} gives an overview of some methods we used in attempt to moderately successfully circumvent those restrictions.
@@
 Another difficulty was getting the universities for the Nobel Prize winners. More on this issue can be found in subsection 2.5.2.
-We also performed a small transformation on the countries, as explained in subsection 2.5.3.
 
@@
 However, there are still 191 Nobel Prize winners for whom we could not find a university both on DBpedia and Nobelprize.org and that we omit for this reason.
-
-\subsubsection{Transforming the countries}
-
-We noticed that some Nobel Prize winners had as a country something like 'Germany (now Poland)'.
-For this reason, we transformed the countries so that everything between parentheses gets removed.
-We also set all countries to lowercase.

### 2016-01-26 project/paper/sections/methodology.tex
extra stap in methodology

@@
 \begin{enumerate}
+\item We decide which persons we exactly want in the training dataset and which persons we want in our research dataset.
 \item We think about what properties of previous Nobel Prize winners might be interesting to incorporate in learning a model.
@@
 This is combined into a training dataset and a research dataset.
-The training dataset consist of all features for scientists and economists that have or have not won a Nobel Prize.
-This can be used to learn a predictive model.
-The research dataset contains the same features, but then for politicians for which we would like to answer the research question.
-\item Some statistics are applied to the training data to assess its quality. For example, because collecting the data is prone to errors, some outlier detection and removal has to be performed.
+The training dataset can be used to learn a predictive model.
+The research dataset is used to answer the research question.
+\item Some statistics are applied to the training dataset to assess its quality. For example, because collecting the data is prone to errors, some outlier detection and removal has to be performed.
 \item The final training dataset is used to learn a model that is able to predict how likely a person is to win a Nobel Prize.

### 2016-01-26 project/paper/sections/analysis.tex
Verslag.

@@
 \noindent Using R we find that the true means are not equal with confidence level $0.05$, which is what we hoped for the model.
-\begin{figure*}
+\begin{figure*}[htb]
     \centering
@@
 \end{figure*}
-\begin{figure*}
+\begin{figure*}[htb]
     \centering
@@
     \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/prodNoOutDensity}
+        \includegraphics[width=\textwidth]{figures/prodNoOutDensity.pdf}
         \caption{After removing outliers}
@@
 
+\subsubsection{Resulting training set}
+The resulting training set contains 5486 examples, of which 559 positive and 5243 negative.
+
 \subsection{Learning a model}
-
-\todo[inline]{Statistieken i.v.m training en research sets hier?}
-
-\todo[inline]{Sectie over difficulties (training data veel negatieve en weinig positieve examples, links die er niet zijn}
+Not only is the data still relatively fuzzy, the problem that we're facing is a hard one.
+Creating a model with high precision and recall will probably be impossible.
+Because of the nature of the test, we want models with a high precision, whereas the recall is less relevant.
+For example, we do not want lots of politicians to be classified as positive, but when is classified as such, we want that prediction to be as accurate as possible.

### 2016-01-26 project/paper/appendices/googlescholar.tex
future work
Wooptie do, veel na te lezen!

@@
-\section{Queries}
-\lstinputlisting[language=SQL, caption=Query 1]{../queries/allnobelwinners.rq}
+\section{Retrieving data from Google Scholar}
+\label{sec:googlescholar}
+
+Retrieving data from Google Scholar is a laborious task.
+This appendix provides our experience and also our tips on how to scrape Google Scholar.
+The idea is mimic a user searching stuff trough a browser.
+
+\subsection{Randomised timing.} Halting random amounts of seconds between successive requests vastly increases the number of requests we can do before getting blocked.
+This happens on two levels: between 15 and 30 seconds between each individual request and another 5 minutes after each 25 requests.
+
+\subsection{Using cookies.} By performing a search via browser and passing the cookies along with our requests, we trick the server into thinking we are using an actual browser.
+
+\subsection{Using proxies.} We created a script that first scrapes a number of proxies from the internet, verifies if they are not yet blocked by Google Scholar and then performs requests using those proxies.
+Note that this is very slow, because most random proxies we find are blocked by Google also.

### 2016-01-26 project/paper/appendices/sparql.tex
Wooptie do, veel na te lezen!

@@
 \begin{enumerate}
-\item \textbf{Links are not broken but queries on them don't work}\\
+\item \textbf{Links are not broken but queries on them don't work.}\\
 Take for example the person Paul R\"ubig.
-There is an data item about him on DBpedia: http://dbpedia.org/page/Paul\_R\"ubig.
-But if you query this specific resource with the query in listing \ref{lst:dbpedia} you will not get any results.
-\lstinputlisting[language=SQL, caption=Query that doesn't work, label={lst:dbpedia}]{queries/dbpedia.rq}
+There is an data item about him on DBpedia: \url{http://dbpedia.org/page/Paul\_Rubig}.
+But if you query this specific resource with the query in Listing~\ref{lst:dbpedia} you will not get any results.
 
-\item \textbf{\texttt{dati.camera.it} doesn't work at all}\\
-In the ToE database there are lot of reference to the Italian linked open data source \texttt{dati.camera.it}.
+\item \textbf{\texttt{dati.camera.it} doesn't work at all.}\\
+In the ToE database there are lot of reference to the Italian linked open data source \url{dati.camera.it}.
 Unfortunately none of our queries seem to give any result.
-Even not for a really simple one, as you can see in listing \ref{lst:dati} and this even though its link \url{http://dati.camera.it/ocd/persona.rdf/p35360} seems to work fine.
+Even not for a really simple one, as given in Listing~\ref{lst:dati} and this even though its link \url{http://dati.camera.it/ocd/persona.rdf/p35360} seems to work fine.
+\end{enumerate}
 
-\lstinputlisting[language=SQL, caption=Query that doesn't work on \texttt{dati.camera.it}, label={lst:dati}]{queries/dati.rq}
-\end{enumerate}
+\lstinputlisting[language=SQL, caption={Query that doesn't work}, label={lst:dbpedia}, xleftmargin=2em]{queries/dbpedia.rq}
+\lstinputlisting[language=SQL, caption={Query that doesn't work on \texttt{dati.camera.it}}, label={lst:dati}, xleftmargin=2em]{queries/dati.rq}

### 2016-01-26 project/paper/sections/analysis.tex
Wooptie do, veel na te lezen!

--- 2016-01-26 project/paper/sections/analysis.tex
@@
 Next, the results are normalised by dividing by the maximal value and rescaled to $[0, 100]$.
-
+\begin{figure*}[!htb]
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{figures/popuInitialBox}
+        \caption{Boxplot}
+        \label{fig:popuInitialBox}
+    \end{subfigure}
+    \quad
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{figures/popuInitialDensity}
+        \caption{Density plot}
+        \label{fig:popuInitialDensity}
+    \end{subfigure}
+    \caption{Distribution plots for raw popularity measure.}
+\end{figure*}
+\begin{figure*}[!htb]
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{figures/popuTransformedBox}
+        \caption{Boxplot}
+        \label{fig:popuTransformedBox}
+    \end{subfigure}
+	~
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{figures/popuTransformedDensity}
+        \caption{Density plot}
+        \label{fig:popuTransformedDensity}
+    \end{subfigure}
+    \caption{Distribution plots for transformed popularity measure.}
+\end{figure*}
+\begin{figure*}[!ht]
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{figures/prodInitialDensity.pdf}
+        \caption{Before outlier removal}
+        \label{fig:prodInitialDensity}
+    \end{subfigure}
+    \quad
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{figures/prodNoOutDensity.pdf}
+        \caption{After removing outliers}
+        \label{fig:prodNoOutDensity}
+    \end{subfigure}
+    \caption{Density plots for productivity measure.}
+    \label{fig:productivity}
+\end{figure*}
 In order to get an initial estimate whether it will be significant in the model, we can compare the mean value for winners and non-winners.
@@
 \noindent Using R we find that the true means are not equal with confidence level $0.05$, which is what we hoped for the model.
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/popuInitialBox.pdf}
-        \caption{Boxplot}
-        \label{fig:popuInitialBox}
-    \end{subfigure}
-    \quad
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/popuInitialDensity}
-        \caption{Density plot}
-        \label{fig:popuInitialDensity}
-    \end{subfigure}
-    \caption{Distribution plots for raw popularity measure.}
-\end{figure*}
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/popuTransformedBox}
-        \caption{Boxplot}
-        \label{fig:popuTransformedBox}
-    \end{subfigure}
-    \quad
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/popuTransformedDensity}
-        \caption{Density plot}
-        \label{fig:popuTransformedDensity}
-    \end{subfigure}
-    \caption{Distribution plots for transformed popularity measure.}
-\end{figure*}
 
@@
 A density plot of before and after removing the outliers is shown in Figure~\ref{fig:productivity}.
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/prodInitialDensity.pdf}
-        \caption{Before outlier removal}
-        \label{fig:prodInitialDensity}
-    \end{subfigure}
-    \quad
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/prodNoOutDensity}
-        \caption{After removing outliers}
-        \label{fig:prodNoOutDensity}
-    \end{subfigure}
-    \caption{Density plots for productivity measure.}
-    \label{fig:productivity}
-\end{figure*}
-
 After removing outliers, we rescale the data to $[0, 100]$ per category. The resulting means are given below.
@@
 
+\subsubsection{Resulting training set}
+The resulting training set contains 5486 examples, of which 559 positive and 5243 negative.
+
 \subsection{Learning a model}
+Using the generated training dataset, we can begin learning a logistic regression model.
+In order to better compare models we learn using different settings, we first need to specify what properties we're looking for.
+The problem at hand is a hard one, so creating a model with high precision and recall will probably be impossible.
+Because of the nature of the test, we want models with a high precision, whereas recall is less relevant.
+For example, we do not want lots of politicians to be classified as positive, but when one is classified as such we want that prediction to be as accurate as possible.
 
-\todo[inline]{Statistieken i.v.m training en research sets hier?}
+In order to validate models, we will use 10-fold cross-validation.
+This is repeated such that the whole dataset was used as an input to the model, trained by other instances.
+From this estimation, we can estimate precision and recall for the model.
 
-\todo[inline]{Sectie over difficulties (training data veel negatieve en weinig positieve examples, links die er niet zijn}
+The initial model uses all features and results in the following weights
+\begin{table}[H]
+\centering
+\begin{tabular}{c|c}
+\textsc{\textbf{Feature}} ($\mathbf{x}$) & \textsc{\textbf{Weight}} ($\boldsymbol{\beta}$)\\ \hline
+\rule{0pt}{4mm}\emph{Intercept}&-2.650\\
+Year&-0.520\\
+University score&-0.285\\
+Popularity&0.789\\
+Productivity&0.068\\
+\end{tabular}
+\end{table}
+\noindent which can be interpreted as 
+\begin{equation*}
+	p(\mathbf{x} = winner) = \frac{1}{1 + e^{-\boldsymbol{\beta}\mathbf{x}}}.
+\end{equation*}
+We immediately notice that Productivity doesn't have much effect on the result, which we suspected would happen from the low $p$ value for $t$-test.
+Performance for this initial model is given in Table~\ref{tbl:initialPerformance}.
+The relevant percentages are shown in bold.
+We notice that the recall is low, as expected.
+This roughly means that if an instance is positive, the model only has 4.59\% chance of discovering this.
+On the other hand, if an instance is predicted positive, there is a 75\% chance that this is correct, which is not bad at all.
+
+\begin{table}
+\centering
+\begin{tabular}{c|l|c|c|c}
+\multicolumn{2}{c|}{} & \multicolumn{2}{c|}{\textsc{Actual}}&\\ \cline{3-4}
+\multicolumn{2}{c|}{\rule{0pt}{4mm}} &No&Yes&Precision\\ \hline
+\multirow{2}{*}{\textsc{Predicted}}&\rule{0pt}{4mm}No&4954&499&90.85\%\\ \cline{2-5}
+\rule{0pt}{4mm}&Yes&8&24&\textbf{75.00\%}\\ \hline
+&\rule{0pt}{4mm}Recall&99.84\%&\textbf{4.59\%}&\\
+\end{tabular}
+\caption{Performance for initial model.}
+\label{tbl:initialPerformance}
+\end{table}
+
+In order to improve on this result, we attempted to exclude some variables from the training set to create different models.
+Another model was constructed by balancing the number of positive and negative examples: all positive examples were included in the training set and an equal number of negative examples was sampled.
+The second method resulted in a model with higher recall (about 60\%), but far lower precision (also about 60\%).
+Because the low precision is not what we want, this model was discarded.
+The first method resulted in a model in which Productivity is not included, for which performance can be found in Table~\ref{tbl:resultingPerformance}.
+The weights of the final model are
+\begin{table}[H]
+\centering
+\begin{tabular}{c|c}
+\textsc{\textbf{Feature}} ($\mathbf{x}$) & \textsc{\textbf{Weight}} ($\boldsymbol{\beta}$)\\ \hline
+\rule{0pt}{4mm}\emph{Intercept}&-2.651\\
+Year&-0.973\\
+University score&-0.299\\
+Popularity&0.899\\
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\begin{tabular}{c|l|c|c|c}
+\multicolumn{2}{c|}{} & \multicolumn{2}{c|}{\textsc{Actual}}&\\ \cline{3-4}
+\multicolumn{2}{c|}{\rule{0pt}{4mm}} &No&Yes&Precision\\ \hline
+\multirow{2}{*}{\textsc{Predicted}}&\rule{0pt}{4mm}No&4956&499&90.85\%\\ \cline{2-5}
+\rule{0pt}{4mm}&Yes&6&24&\textbf{80.00\%}\\ \hline
+&\rule{0pt}{4mm}Recall&99.84\%&\textbf{4.59\%}&\\
+\end{tabular}
+\caption{Performance for final model.}
+\label{tbl:resultingPerformance}
+\end{table}

### 2016-01-26 project/paper/sections/data.tex
Update data.tex

@@
 
-First, we determine features of people that might influence their probability of winning a Nobel Prize.
-They are elaborated in Section~\ref{ssec:features}.
+First, we determine features of people that might influence their probability of winning a Nobel Prize. They are elaborated in Section~\ref{ssec:features}.
+Then, we decide what our training dataset and research dataset should look like in Section 2.2.
 Next, we research whether and where this information can be found.
@@
 \end{itemize}
+
+\subsection{Training dataset and research dataset}
+The positive examples in our training dataset are of course the Nobel Prize winners.
+For the negative examples, we want to take people that were able to win a Nobel Prize but did not.
+Our chosen feature for work productivity does not make much sense for other categories then scientists and economists.
+As we want to learn from consistent data, we take scientists and economists born after 1850 as our negative examples.
+The research dataset contains the politicians for which we want to answer the research question.
+Since the purpose of this project was to use the Semantic Web to answer a research question involving the Talk of Europa database, the research dataset consists of European politicians from this database.
 

### 2016-01-26 project/paper/sections/analysis.tex

@@
 Using the generated training dataset, we can begin learning a logistic regression model.
-In order to better compare models we learn using different settings, we first need to specify what properties we're looking for.
+In order to better compare the models we learn using different settings, we first need to specify what properties we're looking for.
 The problem at hand is a hard one, so creating a model with high precision and recall will probably be impossible.
-Because of the nature of the test, we want models with a high precision, whereas recall is less relevant.
+Because of the nature of the problem, we want models with a high precision, whereas recall is less relevant.
 For example, we do not want lots of politicians to be classified as positive, but when one is classified as such we want that prediction to be as accurate as possible.
@@
 \end{equation*}
-We immediately notice that Productivity doesn't have much effect on the result, which we suspected would happen from the low $p$ value for $t$-test.
+We immediately notice that Productivity doesn't have much effect on the result, which we suspected would happen from the low $p$ value for the $t$-test.
 Performance for this initial model is given in Table~\ref{tbl:initialPerformance}.
@@
 
-In order to improve on this result, we attempted to exclude some variables from the training set to create different models.
-Another model was constructed by balancing the number of positive and negative examples: all positive examples were included in the training set and an equal number of negative examples was sampled.
-The second method resulted in a model with higher recall (about 60\%), but far lower precision (also about 60\%).
+In order to improve on this result, another model was constructed by balancing the number of positive and negative examples: all positive examples were included in the training set and an equal number of negative examples was sampled.
+This method resulted in a model with higher recall (about 60\%), but far lower precision (also about 60\%).
 Because the low precision is not what we want, this model was discarded.
-The first method resulted in a model in which Productivity is not included, for which performance can be found in Table~\ref{tbl:resultingPerformance}.
+Next, we attempted to exclude some variables from the training set to create a better model.
+This resulted in the final model in which Productivity is not included, for which performance can be found in Table~\ref{tbl:resultingPerformance}.
 The weights of the final model are

### 2016-01-26 project/scripts/getLikes.pl
Politician dataset and such!

@@ -7,12 +7,11 @@ use Data::Dumper;
 use List::Util qw(max);
 
 $name = $ARGV[0];
-$access_token = "CAACEdEose0cBAD4PthZAsdoo7iwRYUErLyBXjNh8oxwT2RWWzfyZB13DpkPCju7kCw6ZCNbX3ZBqj404jZCSkOShmgOeL8pYYw7lQiS8l0gNQLm62QZCKZAicDp77jDhTvr6HYvgyQiktsftt2XXd4SDwJeZBbHrC2nxyoSXu0AQqNmYWHV9BhZCYnz7O0ckRBdd9LcLBM14pP2ZChLcZBpUn2f";
+$access_token = "CAACEdEose0cBALUtd3RWhT61HfTF2YRLkvMoUSNGpaGwSZAiAyCs887DauHCN5YMkC7EuOYjUu6E8Ssi5FAZBCevHD4CAH5okwGdGxiOPOCG2k63osgOZCZCHcivBeDhTLC18QrNyfaOdaLK2wLZCzZB4PhHrZATg4LNXQhgdMZAE7TknPb4pzhjKLgXmtwPa0NZCeBMvZAmwmxEiN7Q3efbwS";
 
 sub getLikes {
   ($id) = @_;
   $l_url = URI->new("https://graph.facebook.com/$id");
-
   $l_url->query_form(
     "access_token" => $access_token,,
     "fields" => "likes"
@@ -42,7 +41,6 @@ $json = decode_json $html;
 
 @likes = ();
 foreach $page (@data) {
-
   if ($page->{'name'} =~ /^$name$/) {
     $like = getLikes $page->{'id'};
     push @likes, $like;

### 2016-01-26 project/scripts/mergePoliticians.pl

@@ -1,0 +1,66 @@
+#!/usr/bin/perl
+
+use Data::Dumper;
+
+open $toe, '<', "../data/TOEPoliticians_testData.csv";
+%toe;
+while(<$toe>) {
+  chomp;
+  ($name, $year, $county, $university, $speeches) = split ";", $_;
+  if (defined $toe{$name}) {
+    push $toe{$name}{'universities'}, $university;
+  } else {
+    $toe{$name} = {
+      year => $year,
+      universities => [$university],
+      speeches => $speeches
+    };
+  }
+}
+
+# Read university scores
+open $rf, '<', "../data/rankings_final.csv";
+%rankings;
+while(<$rf>) {
+  chomp;
+  @u = split /;/, $_;
+  $rankings{$u[0]} = $u[1];
+}
+
+for $name (keys %toe) {
+  # Get likes
+  $likes = `perl getLikes.pl \"$name\"`;
+  if ($likes =~ /\d*/) {
+    $toe{$name}{'likes'} = $likes;
+  }
+  $score = 0;
+  $c = 0;
+  foreach $uni (@{$toe{$name}{'universities'}}) {
+    if ($rankings{$uni} > 0) {
+      $score += $rankings{$uni};
+      $c++;
+    }
+  }
+  if ($score > 0) {
+    $score = $score / $c;
+  }
+  $toe{$name}{'score'} = $score;
+  print "$name \t $likes\n";
+}
+
+
+open $out, '>', "../data/finalPoliticians.csv";
+$h = join(";", ('Name', 'Year', 'UniversityScore', 'Productivity', 'Popularity'));
+print $out "$h\n";
+foreach $name (keys %toe) {
+  @properties = (
+    $name,
+    $toe{$name}{'year'},
+    $toe{$name}{'score'},
+    $toe{$name}{'speeches'},
+    $toe{$name}{'likes'}
+  );
+  $p = join(';', @properties);
+  print $out "$p\n";
+}
+close $out;

### 2016-01-26 project/scripts/trainingStatistics.R

@@ -1,0 +1,104 @@
+library(tikzDevice)
+library(plyr)
+
+# Read file
+nobelAll.df <- read.table('finalData.csv', sep = ';', header = TRUE,  quote = "");
+# Remove missing values
+nobel.df <- na.omit(nobelAll.df)
+
+# Number of positive and negative
+sum(nobel.df$Nobel == "yes")
+sum(nobel.df$Nobel == "no")
+
+##############
+# POPULARITY #
+##############
+
+# # Boxplot of popularity
+# tikz('../paper/figures/initialBox.tex', standAlone = TRUE)
+# boxplot(nobel.df$Popularity, axes = F)
+# axis(2,
+#      at = c(0, 5e+06,              1e+07,    1.5e+07),
+#  labels = c(0, "$5 \\times 10^6$", "$10^7$", "$1.5 \\times 10^7$"))
+# box()
+# dev.off()
+# 
+# # Density plot of popularity
+# tikz('../paper/figures/initialDensity.tex', standAlone = TRUE)
+# plot(density(nobel.df$Popularity), main = "",
+#      axes = FALSE,
+#      zero.line = false)
+# axis(1, at = c(0, 10000000, max(nobel.df$Popularity)), 
+#     labels = c(0, "$10^7$",   "$17 \\cdot 10^7$"))
+# axis(2)
+# box()
+# dev.off()
+
+# Log-transform popularity
+nobel.df$LogPopularity = log(nobel.df$Popularity)
+nobel.df$LogPopularity[nobel.df$LogPopularity == -Inf] <- 0
+
+# # Density and boxplot of log-transformed popularity
+# tikz('../paper/figures/transformedBox.tex', standAlone = TRUE)
+# boxplot(nobel.df$LogPopularity, las = 2)
+# dev.off()
+# 
+# tikz('../paper/figures/transformedDensity.tex', standAlone = TRUE)
+# plot(density(nobel.df$LogPopularity), main = "",
+#      zero.line = FALSE)
+# dev.off()
+
+# Standardise by category
+nobel.df$LogPopularityStand <- ave(nobel.df$LogPopularity, 
+                                   nobel.df$Type, 
+                                   FUN = function(x) (x / max(x)) * 100)
+
+var.test(nobel.df$LogPopularityStand[nobel.df$Nobel == "yes"],
+         nobel.df$LogPopularityStand[nobel.df$Nobel == "no"])
+
+# Test if there is sufficient difference in means
[…]

### 2016-01-26 project/paper/sections/results.tex
Results.

\section{Results}
\label{sec:results}
Now that a model is created, we can apply it on our training data. In total, we have 70 politicians for which we found all needed features. The popularity measure for politicians is also transformed using Equation~\ref{eq:logtransform}. Because productivity is not included in the final model, we can discard the number of speeches. Out of those 70 politicians, 4 are classified as positive, although just barely passing the threshold. They are shown, along with their confidence level, in Table~\ref{tbl:confidences}.

\begin{table}[H]
\centering
\begin{tabular}{l|c}
\textsc{\textbf{Name}}&\textsc{\textbf{Confidence}}\\ \hline
\rule{0pt}{4mm}Giorgio Napolitano&0.555\\
Nigel Farage&0.569\\
Matteo Salvini&0.661\\
Jerzy Buzek&0.525
\end{tabular}
\caption{Confidence for positively predicted politicians.}
\label{tbl:confidences}
\end{table}

### 2016-01-26 project/paper/sections/conclusion.tex
Conclusion en results.

\section{Conclusion}

In this report, we wanted to use Linked Open Data, along with other aggregated data, to predict which politicians have a good chance at winning a Nobel Prize. First, we selected some features we though would serve this purpose well and gathered all necessary data. While getting data from SPARQL endpoints is mostly quite straightforward, combining it with other data is not always as easy.

\begin{itemize}
	\item[$\rightarrow$] \textbf{Conclusion 1:} data that is not linked yet, is hard to gather and link.
\end{itemize}

\noindent After analysing the data, we noticed that it had to be cleaned and transformed in order to be used in learning the model.

\begin{itemize}
	\item[$\rightarrow$] \textbf{Conclusion 2:} much publicly available data is \emph{fuzzy} and needs to be thoroughly examined before being put to use.
\end{itemize}

\noindent After we constructed final datasets, we learned and tested a model. Here, we looked for model with high precision, whereas recall didn't matter that much. Not all features performed as expected.

\begin{itemize}
	\item[$\rightarrow$] \textbf{Conclusion 3:} determining good features for difficult learning tasks is hard, especially with limited resources.
\end{itemize}

\noindent While 4 politicians were predicted as positive, we are still in slight doubt about the reliability of these predictions. That being said, the fact that we could positively predict examples, was a huge success nevertheless.

### 2016-01-26 project/paper/sections/results.tex
Conclusion en results.

@@
 They are shown, along with their confidence level, in Table~\ref{tbl:confidences}.
-
 \begin{table}[H]
@@
 \end{table}
+\noindent In order to get an idea of how we get these results, we can look at their values for the different features, as shown in Table~\ref{tbl:posfeatures}.
+\begin{table}[H]
+\centering
+\begin{tabular}{l|c|c|c}
+\textsc{\textbf{Confidence}}&\textsc{\textbf{Year}}&\textsc{\textbf{\shortstack{University\\Score}}}&\textsc{\textbf{Popularity}}\\ \hline
+\rule{0pt}{4mm}0.555&1925&0&75.315\\
+0.569&1964&0&89.375\\
+0.661&1973&0&100\\
+0.525&1940&0&77.964
+\end{tabular}
+\caption{Features for positively predicted politicians from Table~\ref{tbl:confidences}.}
+\label{tbl:posfeatures}
+\end{table}
+\noindent It shows that Popularity is by far the most important feature according to our model.
+Note that a lot of popularity is probably acquired by winning a Nobel Prize, so while being a good indicator for whether someone has won a Nobel Prize, using it for prediction might be dangerous without further interpretation.
+Surprisingly, university score does not play a large role in predicting politicians as positive.
+Intuitively, since the score is based on producing Nobel Prize winners, this should have more influence.

### 2016-01-26 project/scripts/testStatistics.R
Test set statistics.

@@ -1,0 +1,15 @@
+# Read file
+poliAll.df <- read.table('finalPoliticians.csv', sep = ';', header = TRUE,  quote = "");
+# Remove missing values
+poli.df <- na.omit(poliAll.df)
+
+# Transform popularity
+poli.df$Popularity <- log(poli.df$Popularity)
+poli.df$Popularity <- (poli.df$Popularity / max(poli.df$Popularity)) * 100;
+
+# Transform productivity
+poli.df$Productivity <- (poli.df$Productivity / max(poli.df$Productivity)) * 100;
+
+# Write table
+write.table(poli.df, "testingSet.csv", sep = ";",
+            row.names = FALSE);

### 2016-01-26 project/paper/appendices/googlescholar.tex
Appendices.

@@
 This appendix provides our experience and also our tips on how to scrape Google Scholar.
-The idea is mimic a user searching stuff trough a browser.
+The idea is mimic a user searching stuff querying the service trough a browser.
+All in all, it still took us about 4 days to scrape all 6600 results.
 
-\subsection{Randomised timing.} Halting random amounts of seconds between successive requests vastly increases the number of requests we can do before getting blocked.
+\subsection{Randomised timing.} 
+Halting random amounts of seconds between successive requests vastly increases the number of requests we can do before getting blocked.
 This happens on two levels: between 15 and 30 seconds between each individual request and another 5 minutes after each 25 requests.
 
-\subsection{Using cookies.} By performing a search via browser and passing the cookies along with our requests, we trick the server into thinking we are using an actual browser.
+\subsection{Using cookies.} 
+By performing a search via browser and passing the cookies along with our requests, we trick the server into thinking we are using an actual browser.
+It is important that cookies are changed with each request.
+Luckily, the \texttt{HTTP::Cookie} module for Perl automatically supports this.
 
-\subsection{Using proxies.} We created a script that first scrapes a number of proxies from the internet, verifies if they are not yet blocked by Google Scholar and then performs requests using those proxies.
-Note that this is very slow, because most random proxies we find are blocked by Google also.
+\subsection{Using proxies.}
+We created a script that first scrapes a number of proxies from the internet, verifies if they are not yet blocked by Google Scholar and then performs requests using those proxies.
+Note that this is very slow, because most random proxies we find are also blocked by Google.
+
+\subsection{Switching IP addresses.}
+Once all other methods fail, switching IP address is the only viable option.
+An easy way to do this is using mobile networking.
+By setting up a wireless hotspot on a cellphone, we can query Google Scholar trough mobile carrier networks.
+Once detected, toggling mobile internet off and on will get you a new IP address from the provider.

### 2016-01-26 project/scripts/statistics.r

@@ -1,102 +1,0 @@
-library(tikzDevice)
-library(plyr)
-
-# Read file
-nobelAll.df <- read.table('finalData.csv', sep = ';', header = TRUE,  quote = "");
-# Remove missing values
-nobel.df <- na.omit(nobelAll.df)
-
-# Number of positive and negative
-sum(nobel.df$Nobel == "yes")
-sum(nobel.df$Nobel == "no")
-
-##############
-# POPULARITY #
-##############
-
-# # Boxplot of popularity
-# tikz('../paper/figures/initialBox.tex', standAlone = TRUE)
-# boxplot(nobel.df$Popularity, axes = F)
-# axis(2,
-#      at = c(0, 5e+06,              1e+07,    1.5e+07),
-#  labels = c(0, "$5 \\times 10^6$", "$10^7$", "$1.5 \\times 10^7$"))
-# box()
-# dev.off()
-# 
-# # Density plot of popularity
-# tikz('../paper/figures/initialDensity.tex', standAlone = TRUE)
-# plot(density(nobel.df$Popularity), main = "",
-#      axes = FALSE,
-#      zero.line = false)
-# axis(1, at = c(0, 10000000, max(nobel.df$Popularity)), 
-#     labels = c(0, "$10^7$",   "$17 \\cdot 10^7$"))
-# axis(2)
-# box()
-# dev.off()
-
-# Log-transform popularity
-nobel.df$LogPopularity = log(nobel.df$Popularity)
-nobel.df$LogPopularity[nobel.df$LogPopularity == -Inf] <- 0
-
-# # Density and boxplot of log-transformed popularity
-# tikz('../paper/figures/transformedBox.tex', standAlone = TRUE)
-# boxplot(nobel.df$LogPopularity, las = 2)
-# dev.off()
-# 
-# tikz('../paper/figures/transformedDensity.tex', standAlone = TRUE)
-# plot(density(nobel.df$LogPopularity), main = "",
-#      zero.line = FALSE)
-# dev.off()
-
-# Standardise by category
-nobel.df$LogPopularityStand <- ave(nobel.df$LogPopularity, 
-                                   nobel.df$Type, 
-                                   FUN = function(x) (x / max(x)) * 100)
-
-var.test(nobel.df$LogPopularityStand[nobel.df$Nobel == "yes"],
-         nobel.df$LogPopularityStand[nobel.df$Nobel == "no"])
-
-# Test if there is sufficient difference in means
[…]

### 2016-01-26 project/paper/sections/data.tex
Small fix.

@@
 For politicians, the number of speeches they make are perhaps a good indication of how productive they are.
-\emph{Because this is a sensitive subject, Appendix \ref{sec:productivity} provides a thorough discussion of why we chose these features and how the research question is slightly weakened by our assumption.
-Furthermore, in Section~\ref{ssec:quality} on quality assessment, we show why we deem both to be a reasonable proxy by comparing their distributions.}
+\emph{Because this is a sensitive subject, Appendix \ref{sec:productivity} provides a thorough discussion of why we chose these features and how the research question is slightly weakened by our assumption.}
 \item \textbf{Popularity.} A popularity measure is easier to define.

### 2016-01-26 project/paper/appendices/googlescholar.tex
typfouten verbeterd

@@
 This appendix provides our experience and also our tips on how to scrape Google Scholar.
-The idea is mimic a user searching stuff querying the service trough a browser.
+The idea is to mimic a user searching stuff querying the service trough a browser.
 All in all, it still took us about 4 days to scrape all 6600 results.
 
-\subsection{Randomised timing.} 
+\subsection{Randomised timing} 
 Halting random amounts of seconds between successive requests vastly increases the number of requests we can do before getting blocked.
@@
 
-\subsection{Using cookies.} 
+\subsection{Using cookies} 
 By performing a search via browser and passing the cookies along with our requests, we trick the server into thinking we are using an actual browser.
@@
 
-\subsection{Using proxies.}
+\subsection{Using proxies}
 We created a script that first scrapes a number of proxies from the internet, verifies if they are not yet blocked by Google Scholar and then performs requests using those proxies.
@@
 
-\subsection{Switching IP addresses.}
-Once all other methods fail, switching IP address is the only viable option.
+\subsection{Switching IP addresses}
+Once all other methods fail, switching IP addresses is the only viable option.
 An easy way to do this is using mobile networking.
-By setting up a wireless hotspot on a cellphone, we can query Google Scholar trough mobile carrier networks.
+By setting up a wireless hotspot on a cellphone, we can query Google Scholar through mobile carrier networks.
 Once detected, toggling mobile internet off and on will get you a new IP address from the provider.

### 2016-01-26 project/paper/appendices/productivity.tex
Conclusion en results.
typfouten verbeterd

@@
 This information isn't publicly available, however, so we looked at something else.
-Coming straight from the ToE knowledge base, the number of speeches at european parliament seemed a good proxy measure.
+Coming straight from the ToE knowledge base, the number of speeches at the European Parliament seemed a good proxy measure.
 Both are numeric properties which we can normalise to $[0, 100]$.
@@
 \end{center}
+
+\subsection{Additional note}
+After experiments, the productivity feature didn't seem to perform well in building a model and it was therefore excluded.
+The discussion whether it could be used if it were a good feature, however, is still interesting.
